---
title: "facebook clustering"
author: "CCP"
date: "1/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r}
library(tidyverse)
library(data.table)
library(magrittr)
library(janitor)
library(scales)
library(zoo)
library(tseries)
library(forecast)
```

# Data
```{r}
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/data")
text_meta_xwalk <- fread("220109_text_meta_xwalk.csv")
obesity_meta <- fread("220108_facebook_obesity_withindex.csv") %>%
  clean_names()

obesity <- fread("211105_feature_matrix_bert.csv")
lda_topics <- fread("220108_lda_topic_probabilities.csv")
#kmeans <- fread("220108_kmeans_centroids.csv")
#dbscan <- fread("221106_dbscan_labels.csv")
```

# Function
## ADF Test
```{r}
arima_its_adf_test <- function(its_date, 
                      dat, 
                      post_or_interaction = "post") {
  first_date = as.Date(its_date) - 14
  last_date = as.Date(its_date) + 14
  
  dat_filtered <- dat %>%
      dplyr::filter(post_created_date >= first_date &
                    post_created_date <= last_date)
  
  date_seq <- seq.Date(from = as.Date(first_date),
                         length.out = nrow(dat_filtered),
                         by = 1)

  if (post_or_interaction == "post") {
      dat_ts <- ts(as.numeric(dat_filtered$posts_per_day), 
                              start = first_date,
                              frequency = 365)

  } else {
      dat_ts <- ts(as.numeric(dat_filtered$interactions_per_day), 
                                   start = first_date,
                                   frequency = 365)
  }
  
  print(adf.test(dat_ts)) #Stationary data if significant (we want stationary)
}
```

## ARIMA- ITS
```{r}
## Note: If adf.test is not significant, that means data needs to be differenced and this function re-run with difference = TRUE. This function does not difference the data. 
arima_its <- function(its_date, 
                      dat, 
                      difference = NA,
                      pulse = FALSE,
                      step = FALSE,
                      ramp = FALSE,
                      post_or_interaction = "post") {
  print(difference)
  first_date = as.Date(its_date) - 14
  last_date = as.Date(its_date) + 14
  
  dat_filtered <- dat %>%
      dplyr::filter(post_created_date >= first_date &
                    post_created_date <= last_date)
  
  date_seq <- seq.Date(from = as.Date(first_date),
                         length.out = nrow(dat_filtered),
                         by = 1)

  if (post_or_interaction == "post") {
      dat_ts <- ts(as.numeric(dat_filtered$posts_per_day), 
                              start = first_date,
                              frequency = 365)

  } else {
      dat_ts <- ts(as.numeric(dat_filtered$interactions_per_day), 
                                   start = first_date,
                                   frequency = 365)
  }
  
  #print(adf.test(dat_ts)) #Stationary data if significant (we want stationary)

## Step Parameter
  transfer <- c()
  if (step == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    transfer <- cbind(transfer, dat_step)
  }

## Ramp Parameter
  if (ramp == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    dat_ramp <- append(rep(0,
                         length(which(dat_step == 0))),
                     seq(1,
                         length(which(dat_step == 1)),
                         1))
    transfer <- cbind(transfer, dat_ramp)
  }
## Pulse Parameter
  if (pulse == TRUE) {
    dat_pulse <- ifelse(date_seq == its_date, 1, 0)
    transfer <- cbind(transfer, dat_pulse)
  }

  if (!is.na(difference)) {
    print(paste0("Running with differencing of ", difference))
      model_func <- auto.arima(dat_ts,
                               d = difference, #Considers differencing data
                               xreg = transfer)
  } else {
    print("Running with no differencing")
      model_func <- auto.arima(dat_ts,
                               xreg = transfer)
  }

  #print(Box.test(model_func$residuals, 
  #         type = "Ljung-Box")) 

  print(summary(model_func))
  print(confint(model_func))
  print((1-pnorm(abs(model_func$coef)/sqrt(diag(model_func$var.coef))))*2)
}
```

# Assigning Final Label to Eventually Combine Data
```{r}
obesity$corpus_index = seq(1, nrow(obesity))
lda_topics$corpus_index = seq(1, nrow(lda_topics))
#kmeans$corpus_index = seq(1, nrow(kmeans))
#dbscan$corpus_index = seq(1, nrow(dbscan))
```

# Picking Label for LDA Based on Max Prob.
```{r}
set.seed(110295)
lda_topics %<>%
  replace(is.na(.), 0)

lda_topics %<>%
  mutate(lda_topic = colnames(lda_topics)[3:6][max.col(lda_topics[,3:6],
                                                       ties.method="random")])
```

# Combine Feature Matrix and Topic
```{r}
obesity %<>%
  select(-V1, -index) %>%
  left_join(lda_topics, by = "corpus_index")
#180,481 in "0",
#268,856 in "1",
#103,479 in "2",
#77,144 in "3"
```

# Combine Metadata and Feature Matrix
```{r}
pet_page_category <- c("ADOPTION_SERVICE", "ANIMAL_RESCUE_SERVICE", "ANIMAL_SHELTER", "AQUARIUM", "AQUATIC_PET_STORE", "DOG_BREEDER", "DOG_DAY_CARE_CENTER", "DOG_PARK", "DOG_TRAINING", "DOG_WALKER", "EQUESTRIAN_FACILITY", "HORSEBACK_RIDING_SERVICE", "HORSE_TRAINER", "KENNEL", "PET", "PETTING_ZOO", "PET_ADOPTION_SERVICE", "PET_BREEDER", "PET_CAFE", "PET_GROOMER", "PET_SERVICE", "PET_SITTER", "PET_STORE", "PET_SUPPLIES", "REPTILE_PET_STORE", "ZOO")
obesity_meta %<>%
  filter(!(page_category %in% pet_page_category))

obesity_meta %<>%
  as.data.frame()

# Final Goal: Combine Meta and Obesity
#obesity$corpus_index = seq(1, nrow(obesity))
obesity_meta$matching_index <- seq(0, nrow(obesity_meta)-1)

topics_metadata_combo <- obesity %>%
  select(A, lda_topic) %>%
  left_join(text_meta_xwalk,
            by = c("A" = "V2")) %>%
  left_join(obesity_meta,
            by = c("V3" = "matching_index"))
```

# Assigning a Topic Label to Each Post
```{r}
topics_metadata_xwalk <- topics_metadata_combo %>%
  group_by(V3, lda_topic) %>%
  summarise(number_of_sentences_per_lda_topic_per_post = n()) %>%
  ungroup() %>%
  group_by(V3) %>%
  mutate(max_count_of_topic = max(number_of_sentences_per_lda_topic_per_post)) %>%
  filter(number_of_sentences_per_lda_topic_per_post == max_count_of_topic)

obesity_meta %<>%
  left_join(topics_metadata_xwalk, 
            by = c("matching_index" = "V3"))

obesity_meta_with_topic <- obesity_meta %>%
  filter(!is.na(lda_topic))

#head(obesity_meta_with_topic) #241,113
```

# Most Popular Post Per Topic
```{r}
obesity_meta_with_topic %<>%
    mutate(total_interactions_numeric =
             as.numeric(str_remove_all(total_interactions, 
                                       " ")))
obesity_meta_with_topic %>%
  group_by(lda_topic) %>%
  summarise(max_total_interaction = max(total_interactions_numeric,
                                         na.rm = TRUE)) 
#0: 180,189
# 1: 414,058
# 2: 190,733
# 3 31,942
```

# Plotting
```{r}
obesity_meta_with_topic %>%
  group_by(lda_topic, post_created_date) %>%
  summarise(count_per_day = n()) %>%
  filter(!is.na(post_created_date),
         post_created_date >= as.Date("2020-01-06"),
         post_created_date <= as.Date("2020-10-08")) %>%
  ggplot(aes(x = post_created_date,
             y = count_per_day,
             color = lda_topic)) +
  geom_line() +
  geom_vline(xintercept = c(as.Date("2020-01-20"),
                            as.Date("2020-03-11"),
                            as.Date("2020-05-19"),
                            as.Date("2020-10-02")),
             linetype = "dashed") + 
  facet_wrap(~lda_topic) + 
  scale_y_continuous(labels = comma) + 
  scale_color_manual(values = c("#A0CBE8",
                                "#FFBE7D",
                                "#8CD17D",
                                "#D4A6C8")) +
  theme_classic() +
  theme(legend.position = "none") + 
  labs(x = "Date",
       y = "Count",
       title = "Number of Posts per Topic Per Day",
       color = "LDA Topic")
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/figures")
ggsave("220112_topics_per_day_facet.tiff",
       width = 7.25, 
       height = 4.51)
```

# Metadata Analysis
```{r}
obesity_meta_with_topic_restricted_dates <- obesity_meta_with_topic %>%
    filter(!is.na(post_created_date),
           post_created_date >= as.Date("2020-01-06"),
           post_created_date <= as.Date("2020-10-08"))

# Top One: page_name, page_category, page_admin_top_country,  
# Average and SD: likes_at_posting, followers_at_posting, total_interactions, likes,
#comments, shares, love, wow, haha, sad, angry, care, post_views, total_views
obesity_meta_with_topic_restricted_dates %>%
  group_by(lda_topic) %>%
  summarise(n())

for (t in c("page_name", "page_category", "page_admin_top_country")) {
  print(t)
  print(obesity_meta_with_topic_restricted_dates %>%
    group_by(lda_topic, get(t)) %>%
    summarize(count = n()) %>%
    #filter(`get(t)` != "none",
    #       `get(t)` != "") %>%
    arrange(desc(count)) %>%
    filter(row_number() == 1))
}

for (t in c("likes_at_posting", "followers_at_posting", "total_interactions", 
            "likes", "comments", "shares", "love", "wow", "haha", "sad", "angry", 
            "care", "post_views", "total_views")) {
  print(obesity_meta_with_topic_restricted_dates %>%
    group_by(lda_topic) %>%
    summarize(average = mean(get(t), 
                             na.rm = TRUE),
              stdev = sd(get(t), 
                         na.rm = TRUE),
              var = t))
}
```

# Evaluating Number of LDA Clusters Over Time
## Plotting
```{r}
obesity_meta_with_topic_restricted_dates <- obesity_meta_with_topic %>%
  group_by(lda_topic, post_created_date) %>%
  summarise(count_per_day = n()) %>%
  filter(!is.na(post_created_date),
         post_created_date >= as.Date("2020-01-06"),
         post_created_date <= as.Date("2020-10-08"))

obesity_meta_with_topic_restricted_dates %>%
  ggplot(aes(x = post_created_date,
             y = count_per_day,
             color = lda_topic)) +
  geom_line() +
  geom_vline(xintercept = c(as.Date("2020-01-20"),
                            as.Date("2020-03-11"),
                            as.Date("2020-05-19"),
                            as.Date("2020-10-02")),
             linetype = "dashed") + 
  facet_wrap(~lda_topic) + 
  scale_y_continuous(labels = comma) + 
  scale_color_manual(values = c("#A0CBE8",
                                "#FFBE7D",
                                "#8CD17D",
                                "#D4A6C8")) +
  theme_classic() +
  theme(legend.position = "none") + 
  labs(x = "Date",
       y = "Count",
       title = "Number of Posts per Topic Per Day",
       color = "LDA Topic")
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/figures")
ggsave("220112_topics_per_day_facet.tiff",
       width = 7.25, 
       height = 4.51)
```

## Running ARIMA
### Checking if Stationary
```{r}
list_of_its_dates <- c(as.Date("2020-01-20"),
                       as.Date("2020-03-11"),
                       as.Date("2020-05-19"),
                       as.Date("2020-10-02"))

topics_per_day <- obesity_meta_with_topic_restricted_dates %>%
  group_by(lda_topic, post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  filter(!is.na(post_created_date))

topics_per_day_0 <- topics_per_day %>%
  filter(lda_topic == 0)
topics_per_day_1 <- topics_per_day %>%
  filter(lda_topic == 1)
topics_per_day_2 <- topics_per_day %>%
  filter(lda_topic == 2)
topics_per_day_3 <- topics_per_day %>%
  filter(lda_topic == 3)

dfs <- c("topics_per_day_0", "topics_per_day_1", "topics_per_day_2", "topics_per_day_3")

for (d in list_of_its_dates) {
  print(as.Date(d))
  for (df in dfs) {
    print(df)
    arima_its_adf_test(d, get(df))
  }
}
```

### Checking Which Transfer Functions to Use
```{r}
for (df in dfs) {
  for (d in list_of_its_dates) {
    if (d %in% c(as.Date("2020-01-20"), as.Date("2020-10-02")) | 
        (d == as.Date("2020-03-11") & df %in% c("topics_per_day_0", "topics_per_day_3")) |
        (d == as.Date("2020-05-19") & df == "topics_per_day_1")){
      diff = 1
    } else if (d == as.Date("2020-03-11") & df == "topics_per_day_1") {
      diff == 2
    } else if (d == as.Date("2020-03-11") & df == "topics_per_day_2") {
      diff == 3
    } else {
      diff = NA
    }
    
    print(as.Date(d))
    print(df)
    print("pulse only")
    arima_its(d, get(df), pulse = TRUE,
              difference = diff)
    print("**********")
    
    print("step only")
    arima_its(d, get(df), step = TRUE,
              difference = diff)
    print("**********")
    
    print("ramp only")
    arima_its(d, get(df), ramp = TRUE,
              difference = diff)
    print("**********")
    
    print("pulse + step only")
    arima_its(d, get(df), 
              pulse = TRUE, 
              step = TRUE,
              difference = diff)
    print("**********")
    
    print("pulse + ramp only")
    arima_its(d, get(df), 
              pulse = TRUE, ramp = TRUE,
              difference = diff)
    print("**********")
    
    print("step + ramp only")
    arima_its(d, get(df), 
              step = TRUE, ramp = TRUE,
              difference = diff)
    print("**********")
    
    print("all")
    arima_its(d, get(df),
              pulse = TRUE, step = TRUE, ramp = TRUE,
              difference = diff)
    print("**********")
  }
}
```

### Running Models
```{r}
# January 20th
for (df in dfs) {
  print(df)
  if (df == "topics_per_day_2") {
    arima_its(as.Date("2020-01-20"),
              get(df),
              difference = 1,
              pulse = TRUE)
  }
  else {
        arima_its(as.Date("2020-01-20"),
              get(df),
              difference = 1,
              step = TRUE)
  }
}

# March 11th
for (df in dfs) {
  print(df)
  if (df == "topics_per_day_1") {
    diff = 2
  } else if (df == "topics_per_day_2") {
    diff = 3
  } else {
    diff = 1
  }
  if (df == "topics_per_day_2") {
    arima_its(as.Date("2020-03-11"),
              get(df),
              difference = diff,
              pulse = TRUE)
  }
  else if (df == "topics_per_day_3") {
        arima_its(as.Date("2020-03-11"),
              get(df),
              difference = diff,
              pulse = TRUE,
              step = TRUE)
  } else {
    arima_its(as.Date("2020-03-11"),
              get(df),
              difference = diff,
              step = TRUE)
  }
}

# May 19th
for (df in dfs) {
  print(df)
  if (df == "topics_per_day_1") {
    diff = 1
  } else {
    diff = NA
  }
  if (df == "topics_per_day_1") {
    arima_its(as.Date("2020-05-19"),
              get(df),
              difference = diff,
              pulse = TRUE)
  }
  
  else {
    arima_its(as.Date("2020-05-19"),
              get(df),
              difference = diff,
              step = TRUE, pulse = TRUE, ramp = TRUE)
  }
}

# October 2nd
for (df in dfs) {
  print(df)
  arima_its(as.Date("2020-10-02"),
              get(df),
              difference = 1,
              pulse = TRUE)
}
```

## Running ARIMA
### Checking if Stationary
```{r}
list_of_its_dates <- c(as.Date("2020-01-20"),
                       as.Date("2020-03-11"),
                       as.Date("2020-05-19"),
                       as.Date("2020-10-02"))

topics_per_day <- obesity_meta_with_topic_restricted_dates %>%
  group_by(lda_topic, post_created_date) %>%
  summarise(posts_per_day = sum(total_interactions_numeric)) %>%
  filter(!is.na(post_created_date))

topics_per_day_0 <- topics_per_day %>%
  filter(lda_topic == 0)
topics_per_day_1 <- topics_per_day %>%
  filter(lda_topic == 1)
topics_per_day_2 <- topics_per_day %>%
  filter(lda_topic == 2)
topics_per_day_3 <- topics_per_day %>%
  filter(lda_topic == 3)

dfs <- c("topics_per_day_0", "topics_per_day_1", "topics_per_day_2", "topics_per_day_3")

for (d in list_of_its_dates) {
  print(as.Date(d))
  for (df in dfs) {
    print(df)
    arima_its_adf_test(d, get(df))
  }
}
```

### Checking Which Transfer Functions to Use
```{r}
for (df in dfs) {
  for (d in list_of_its_dates) {
    if (d == as.Date("2020-01-20") & df != "topics_per_day_3") {
      diff = NA
    } else {
      diff = 1
    }
    
    print(as.Date(d))
    print(df)
    print("pulse only")
    arima_its(d, get(df), pulse = TRUE,
              difference = diff)
    print("**********")
    
    print("step only")
    arima_its(d, get(df), step = TRUE,
              difference = diff)
    print("**********")
    
    print("ramp only")
    arima_its(d, get(df), ramp = TRUE,
              difference = diff)
    print("**********")
    
    print("pulse + step only")
    arima_its(d, get(df), 
              pulse = TRUE, 
              step = TRUE,
              difference = diff)
    print("**********")
    
    print("pulse + ramp only")
    arima_its(d, get(df), 
              pulse = TRUE, ramp = TRUE,
              difference = diff)
    print("**********")
    
    print("step + ramp only")
    arima_its(d, get(df), 
              step = TRUE, ramp = TRUE,
              difference = diff)
    print("**********")
    
    print("all")
    arima_its(d, get(df),
              pulse = TRUE, step = TRUE, ramp = TRUE,
              difference = diff)
    print("**********")
  }
}
```

### Running Models
```{r}
# January 20th
for (df in dfs) {
  print(df)
  if (df == "topics_per_day_2") {
    arima_its(as.Date("2020-01-20"),
              get(df),
              pulse = TRUE)
  }
  else if (df == "topics_per_day_3") {
      arima_its(as.Date("2020-01-20"),
              get(df),
              difference = 1,
              step = TRUE)
  } else {
        arima_its(as.Date("2020-01-20"),
              get(df),
              step = TRUE)
  }
}

# March 11th
for (df in dfs) {
  print(df)
  if (df == "topics_per_day_0") {
    arima_its(as.Date("2020-03-11"),
              get(df),
              difference = 1,
              pulse = TRUE)
  }
  else if (df == "topics_per_day_3") {
        arima_its(as.Date("2020-03-11"),
              get(df),
              difference = 1,
              step = TRUE)
  } else {
    arima_its(as.Date("2020-03-11"),
              get(df),
              difference = 1,
              ramp = TRUE)
  }
}

# May 19th
for (df in dfs) {
  print(df)
  if (df == "topics_per_day_0") {
    arima_its(as.Date("2020-05-19"),
              get(df),
              difference = 1,
              step = TRUE, ramp = TRUE)
    
  } else if (df == "topics_per_day_1") {
    arima_its(as.Date("2020-05-19"),
              get(df),
              difference = 1,
              pulse = TRUE)
  }  else if (df == "topics_per_day_2") {
    arima_its(as.Date("2020-05-19"),
              get(df),
              difference = 1,
              pulse = TRUE, step = TRUE)
  } else {
    arima_its(as.Date("2020-05-19"),
              get(df),
              difference = 1,
              step = TRUE)
  }
}

# October 2nd
for (df in dfs) {
  print(df)
  if (df == "topics_per_day_2") {
    arima_its(as.Date("2020-10-02"),
              get(df),
              difference = 1,
              pulse = TRUE, step = TRUE, ramp = TRUE)
  }
  else if (df == "topics_per_day_3") {
        arima_its(as.Date("2020-10-02"),
              get(df),
              difference = 1,
              step = TRUE)
  } else {
    arima_its(as.Date("2020-10-02"),
              get(df),
              difference = 1,
              pulse = TRUE)
  }
}
```

