---
title: "facebook clustering"
author: "CCP"
date: "1/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r}
library(tidyverse)
library(data.table)
library(magrittr)
library(janitor)
library(scales)
library(zoo)
library(tseries)
library(forecast)
library(tidytext)
```

# Data
```{r}
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/data")
obesity_topics <- fread("220331_obesity_with_topics_instagram.csv") %>%
  clean_names()

```

# Function
## ARIMA- ITS
```{r}
## Note: If adf.test is not significant, that means data needs to be differenced and this function re-run with difference = TRUE. This function does not difference the data. 
arima_its <- function(its_date, 
                      dat, 
                      difference = NA,
                      pulse = FALSE,
                      step = FALSE,
                      ramp = FALSE,
                      post_or_interaction = "post",
                      aic_only = FALSE) {
  print(difference)
  first_date = as.Date(its_date) - 14
  last_date = as.Date(its_date) + 14
  
  dat_filtered <- dat %>%
      dplyr::filter(post_created_date >= first_date &
                    post_created_date <= last_date)
  
  date_seq <- seq.Date(from = as.Date(first_date),
                         length.out = nrow(dat_filtered),
                         by = 1)

  if (post_or_interaction == "post") {
      dat_ts <- ts(as.numeric(dat_filtered$posts_per_day), 
                              start = first_date,
                              frequency = 365)

  } else {
      dat_ts <- ts(as.numeric(dat_filtered$interactions_per_day), 
                                   start = first_date,
                                   frequency = 365)
  }
  
  #print(adf.test(dat_ts)) #Stationary data if significant (we want stationary)

## Step Parameter
  transfer <- c()
  if (step == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    transfer <- cbind(transfer, dat_step)
  }

## Ramp Parameter
  if (ramp == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    dat_ramp <- append(rep(0,
                         length(which(dat_step == 0))),
                     seq(1,
                         length(which(dat_step == 1)),
                         1))
    transfer <- cbind(transfer, dat_ramp)
  }
## Pulse Parameter
  if (pulse == TRUE) {
    dat_pulse <- ifelse(date_seq == its_date, 1, 0)
    transfer <- cbind(transfer, dat_pulse)
  }

  if (!is.na(difference)) {
    print(paste0("Running with differencing of ", difference))
      model_func <- auto.arima(dat_ts,
                               d = difference, #Considers differencing data
                               xreg = transfer)
  } else {
    print("Running with no differencing")
      model_func <- auto.arima(dat_ts,
                               xreg = transfer)
  }

  #print(Box.test(model_func$residuals, 
  #         type = "Ljung-Box")) 

  if (aic_only == TRUE) {
    return(model_func$aic)
  }
  else {
    print(summary(model_func))
    print(confint(model_func))
    print((1-pnorm(abs(model_func$coef)/sqrt(diag(model_func$var.coef))))*2) 
  }
}
```

# Number of Posts per Topic
```{r}
nrow(obesity_topics) #18,129
View(obesity_topics %>%
  group_by(topics) %>%
  count())

obesity_topics %<>%
  dplyr::filter(topics >= 0 & topics <= 10 & topics != 2) #17,907 posts
```

# Number of Posts per Topic
```{r}
obesity_topics %<>%
  as.data.frame()

obesity_topics %<>%
  mutate(topic_renamed = paste0("Topic: ", topics))

View(obesity_topics %>%
  group_by(topic_renamed) %>%
  summarise(count = n()))

obesity_topics %>%
  group_by(topic_renamed) %>%
  summarise(count = n()) %>%
  ggplot(aes(y = reorder(topic_renamed, count),
             x = count)) +
  geom_bar(stat = "identity",
           color = "black",
           fill = "#E1306C") +
  theme_classic() +
  labs(x = "Count",
       y = "Topic Number",
       title = "Number of Posts per LDA Topic - Instagram")
#setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/figures")
#ggsave("220201_topic_counts_instagram.tiff",
#       width = 7.25,
#       height = 4.51)
```

# Distribution of Interactions per Topic
```{r}
obesity_topics %<>%
    mutate(total_interactions_numeric =
             as.numeric(str_remove_all(total_interactions, 
                                       " ")))

View(obesity_topics %>%
       group_by(topic_renamed) %>%
       summarise(median(total_interactions_numeric,
                     na.rm = TRUE),
              quantile(total_interactions_numeric,
                       0.25,
                       na.rm = TRUE),
              quantile(total_interactions_numeric,
                       0.75,
                       na.rm = TRUE)))
     
obesity_topics %>%
  group_by(topic_renamed) %>%
  filter(total_interactions_numeric > 0) %>%
  mutate(median_total_interaction = median(log10(total_interactions_numeric),
                                         na.rm = TRUE)) %>%
  ggplot(aes(x = log10(total_interactions_numeric),
             y = reorder(topic_renamed, 
                         median_total_interaction))) +
  geom_boxplot(color = "black",
               fill = "#E1306C") +
  theme_classic() +
  labs(x = "Log (Base 10) Interactions",
       y = "Topic Number",
       title = "Distribution of Interactions per LDA Topic - Instagram")
#setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/figures")
#ggsave("220201_interaction_distribution_facebook.tiff",
#       width = 7.25,
#       height = 4.51)
```

## By Interaction Type
```{r}
obesity_topics %>%
  group_by(topic_renamed) %>%
  select(likes, comments, views, topic_renamed) %>%
  melt(id = "topic_renamed") %>%
  mutate(value = as.numeric(gsub(" ", "", value)),
         log_value = log10(value)) %>%
  filter(value > 0) %>%
  ggplot(aes(x = reorder_within(topic_renamed,
                                log_value,
                                variable,
                                median),
             y = log_value,
             fill = variable)) +
  geom_boxplot(color = "black",
               position = position_dodge(width = 2)) +
  theme_classic() +
  facet_wrap(~variable,
             scales = "free_y") +
  scale_x_reordered() +
  scale_fill_manual(values = c("#A0CBE8",
                                "#F28E2B",
                                "#8CD17D")) + 
  coord_flip() + 
  theme(axis.text.y = element_text(size = 6),
        legend.position = "none") +
  labs(y = "Log (Base 10) Count",
       x = "Topic",
       title = "Distribution of Interactions by Type and Topic - Instagram")
#setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/figures")
#ggsave("220304_interaction_distribution_instagram_facet.tiff",
#       width = 7.25,
#       height = 4.51)

View(obesity_topics %>%
  group_by(topic_renamed) %>%
  select(likes, comments, views, topic_renamed) %>%
  melt(id = "topic_renamed") %>%
  mutate(value = as.numeric(gsub(" ", "", value)),
         log_value = log10(value)) %>%
  group_by(topic_renamed, variable) %>%
  summarise(median(value, na.rm = TRUE),
            quantile(value, 0.25, na.rm = TRUE),
            quantile(value, 0.75, na.rm = TRUE)))
```

# Plot of Count per Day
```{r}
obesity_topics %>%
  mutate(date_date = as.Date(post_created_date)) %>%
  group_by(topic_renamed, date_date) %>%
  summarise(count_per_day = n()) %>%
  mutate(topic_renamed = factor(topic_renamed,
                                    levels = c("Topic: 0", "Topic: 1", "Topic: 3", "Topic: 4", "Topic: 5", "Topic: 6", "Topic: 7", "Topic: 8", "Topic: 9", "Topic: 10")),
         topics_facet = case_when(
           topic_renamed == "Topic: 0" ~ "Weight Loss Stories",
           topic_renamed == "Topic: 1" ~ "COVID-19",
           topic_renamed == "Topic: 3" ~ "Keto Diet",
           topic_renamed == "Topic: 4" ~ "Weight Loss Program",
           topic_renamed == "Topic: 5" ~ "Calories",
           topic_renamed == "Topic: 6" ~ "Bariatric Surgery",
           topic_renamed == "Topic: 7" ~ "Sugar",
           topic_renamed == "Topic: 8" ~ "Response to UK Gov. Policy",
           topic_renamed == "Topic: 9" ~ "Childhood Obesity",
           topic_renamed == "Topic: 10" ~ "Sleep")) %>%
  filter(date_date >= as.Date("2020-01-06"),
         date_date <= as.Date("2020-10-16")) %>%
  ggplot(aes(x = date_date,
             y = count_per_day,
             color = topics_facet)) +
  geom_vline(xintercept = c(as.Date("2020-01-20"),
                            as.Date("2020-03-11"),
                            as.Date("2020-05-19"),
                            as.Date("2020-10-02")),
             linetype = "dashed") + 
  geom_line(size = 0.5) +
  facet_wrap(~topics_facet) + 
  scale_color_manual(values = c("#9E0142",
                                "#D53E4F",
                                "#F46D43",
                                "#FDAE61",
                                "#FEE08B",
                                "#ABDDA4", 
                                "#66C2A5",
                                "#3288BD",
                                "#5E4FA2",
                                "grey")) +
  theme_classic() +
  theme(legend.position = "none") + 
  labs(x = "Date",
       y = "Count",
       title = "Number of Posts per Topic Per Day - Instagram")
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/figures")
ggsave("220412_topics_per_day_facet_instagram.tiff",
       width = 7.25, 
       height = 4.51)
```

# Metadata Analysis
```{r}
obesity_date_restricted <- obesity_topics %>%
    filter(!is.na(post_created_date),
           post_created_date >= as.Date("2020-01-06"),
           post_created_date <= as.Date("2020-10-16"))

View(obesity_topics %>%
  group_by(topic_renamed) %>%
  mutate(denominator = n()) %>%
  group_by(topic_renamed, type) %>%
  summarise(count = n(),
            percent = round(count/denominator*100, 2)) %>%
  arrange(topic_renamed, desc(count)) %>%
  distinct(.))

View(obesity_topics %>%
  group_by(topic_renamed) %>%
  select(likes, comments, views, followers_at_posting, topic_renamed) %>%
  melt(id = "topic_renamed") %>%
  mutate(value = as.numeric(gsub(" ", "", value)),
         log_value = log10(value)) %>%
  group_by(topic_renamed, variable) %>%
  summarise(median(value, na.rm = TRUE),
            quantile(value, 0.25, na.rm = TRUE),
            quantile(value, 0.75, na.rm = TRUE)))
```

# Topic Distribution Around Key Dates
```{r}
topic_distribution_jan <- obesity_topics %>%
  filter(post_created_date <= as.Date("2020-01-20") + 14) %>%
  group_by(topic_renamed) %>%
  count() %>%
  mutate(date = "Jan. 6 - Feb. 3, 2020")

topic_distribution_mar <- obesity_topics %>%
  filter(post_created_date <= as.Date("2020-03-11") + 14 &
           post_created_date >= as.Date("2020-03-11") - 14) %>%
  group_by(topic_renamed) %>%
  count() %>%
  mutate(date = "Feb. 26 - Mar. 25, 2020")

topic_distribution_may <- obesity_topics %>%
  filter(post_created_date <= as.Date("2020-05-19") + 14 &
           post_created_date >= as.Date("2020-05-19") - 14) %>%
  group_by(topic_renamed) %>%
  count() %>%
  mutate(date = "May 5 - June 2, 2020")

topic_distribution_oct <- obesity_topics %>%
  filter(post_created_date <= as.Date("2020-10-02") + 14 &
           post_created_date >= as.Date("2020-10-02") - 14) %>%
  group_by(topic_renamed) %>%
  count() %>%
  mutate(date = "Sept. 18 - Oct. 16, 2020")

topic_distribution <- rbind(topic_distribution_jan, topic_distribution_mar, topic_distribution_may, topic_distribution_oct)

topic_distribution %>%
  arrange(desc(n)) %>%
  mutate(topic_renamed = factor(topic_renamed,
                                    levels = c("Topic: 0", "Topic: 1", "Topic: 3", "Topic: 4", "Topic: 5", "Topic: 6", "Topic: 7", "Topic: 8", "Topic: 9", "Topic: 10")),
         topics_facet = case_when(
           topic_renamed == "Topic: 0" ~ "Weight Loss Stories",
           topic_renamed == "Topic: 1" ~ "COVID-19",
           topic_renamed == "Topic: 3" ~ "Keto Diet",
           topic_renamed == "Topic: 4" ~ "Weight Loss Program",
           topic_renamed == "Topic: 5" ~ "Calories",
           topic_renamed == "Topic: 6" ~ "Bariatric Surgery",
           topic_renamed == "Topic: 7" ~ "Sugar",
           topic_renamed == "Topic: 8" ~ "Response to UK Gov. Policy",
           topic_renamed == "Topic: 9" ~ "Childhood Obesity",
           topic_renamed == "Topic: 10" ~ "Sleep"),
         date = relevel(as.factor(date), ref = "Jan. 6 - Feb. 3, 2020")) %>%
  ggplot(aes(x = n,
             y = reorder_within(topics_facet,
                                n,
                                date), 
             fill = topics_facet)) +
  geom_bar(stat = "identity", color = "black") +
  facet_wrap(~date, scales = "free_y") +
  theme_classic() + 
  scale_y_reordered() +
  scale_fill_manual(values = c("#9E0142",
                                "#D53E4F",
                                "#F46D43",
                                "#FDAE61",
                                "#FEE08B",
                                "#ABDDA4", 
                                "#66C2A5",
                                "#3288BD",
                                "#5E4FA2",
                                "grey")) +
  theme(legend.position = "none") +
  labs(x = "Count",
       y = "Topic",
       title = "Distribution of Posts Around Each Date of Interest")
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/figures")
ggsave("220330_topics_per_time_period_aggregate.tiff",
       width = 7.25, 
       height = 4.51)
```

# Evaluating Number of LDA Clusters Over Time
## Running ARIMA
### Checking if Stationary
```{r}
list_of_its_dates <- c(as.Date("2020-01-20"),
                       as.Date("2020-03-11"),
                       as.Date("2020-05-19"),
                       as.Date("2020-10-02"))

topics_per_day <- obesity_date_restricted %>%
  group_by(topics, post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  filter(!is.na(post_created_date))

for (i in min(topics_per_day$topics):max(topics_per_day$topics)) {
  if (i == 2) {
    next
  }
  else {assign(paste0("topics_per_day_", i), topics_per_day %>%
           filter(topics == i))}
}

dfs <- c("topics_per_day_0", "topics_per_day_1", "topics_per_day_3", "topics_per_day_4", "topics_per_day_5", "topics_per_day_6", "topics_per_day_7", "topics_per_day_8", "topics_per_day_9", "topics_per_day_10") #Not running ARIMA on 12, 13, 14 -- too few posts
```

### Checking Which Transfer Functions to Use
```{r}
aic_table <- NULL
for (df in dfs) {
  for (d in list_of_its_dates) {
    if (d == 18281 & df %in% c("topics_per_day_1", "topics_per_day_8") |
        d == 18332 & df %in% c("topics_per_day_4", "topics_per_day_8") |
        d == 18401 & df %in% c("topics_per_day_4", "topics_per_day_10") |
        d == 18537 & df %in% c("topics_per_day_4", "topics_per_day_8")) {
      next
    }
    print(as.Date(d))
    print(df)
    aic_pulse = arima_its(d, get(df), pulse = TRUE, aic_only = TRUE)

    aic_step = arima_its(d, get(df), step = TRUE, aic_only = TRUE)

    aic_ramp = arima_its(d, get(df), ramp = TRUE, aic_only = TRUE)

    aic_pulse_step = arima_its(d, get(df), 
              pulse = TRUE, 
              step = TRUE, aic_only = TRUE)

    aic_pulse_ramp =  arima_its(d, get(df), 
                                pulse = TRUE, ramp = TRUE, aic_only = TRUE)

    aic_step_ramp = arima_its(d, get(df), 
                              step = TRUE, ramp = TRUE, aic_only = TRUE)

    aic_all = arima_its(d, get(df),
              pulse = TRUE, step = TRUE, ramp = TRUE, aic_only = TRUE)
    aic_table <- rbind(aic_table, 
                       cbind(df, d, 
                             aic_pulse, aic_step, aic_ramp, aic_pulse_step, aic_pulse_ramp, 
                             aic_step_ramp, aic_all))
  }
}

aic_table %<>%
  as.data.frame()

aic_table$best_transfer_function <- apply(aic_table, 1, FUN = function(x) names(x)[which.min(x)])

aic_table %<>%
  mutate_at(c("aic_pulse", "aic_step", "aic_ramp", "aic_pulse_step", "aic_pulse_ramp", "aic_step_ramp", "aic_all"),
            as.numeric) %>%
  rowwise() %>%
  mutate(best_aic = round(min(aic_pulse, aic_step, aic_ramp, aic_pulse_step, aic_pulse_ramp, aic_step_ramp, aic_all), 3)) %>%
  as.data.frame()

View(aic_table %>% select(df, d, best_aic, best_transfer_function))
```

### Running Models
```{r}
# January 20th
for (df in dfs) {
  print(df)
  p = FALSE
  r = FALSE
  s = FALSE
  if (df %in% c("topics_per_day_3", "topics_per_day_7")) {
    p = TRUE
  } 
  if (df %in% c("topics_per_day_0", "topics_per_day_5", "topics_per_day_6", "topics_per_day_9", "topics_per_day_10")) {
    s = TRUE
  } 
  if (df %in% c("topics_per_day_4")) {
    r = TRUE
  } 
  if (df %in% c("topics_per_day_1", "topics_per_day_8")) {
    next
  }
  arima_its(as.Date("2020-01-20"),
            get(df),
            pulse = p,
            step = s,
            ramp = r)
}

# March 11th
for (df in dfs) {
  print(df)
  p = FALSE
  r = FALSE
  s = FALSE
  if (df %in% c("topics_per_day_1", "topics_per_day_5")) {
    p = TRUE
  } 
  if (df %in% c("topics_per_day_6", "topics_per_day_9", "topics_per_day_10")) {
    s = TRUE
  } 
  if (df %in% c("topics_per_day_0", "topics_per_day_3", "topics_per_day_7")) {
    r = TRUE
  } 
  if (df %in% c("topics_per_day_4", "topics_per_day_8")) {
    next
  }
  arima_its(as.Date("2020-03-11"),
            get(df),
            pulse = p,
            step = s,
            ramp = r)
}

# May 19th
for (df in dfs) {
  print(df)
  p = FALSE
  r = FALSE
  s = FALSE
  if (df %in% c("topics_per_day_6", "topics_per_day_7")) {
    p = TRUE
  } 
  if (df %in% c("topics_per_day_3", "topics_per_day_5")) {
    s = TRUE
  } 
  if (df %in% c("topics_per_day_0", "topics_per_day_1", "topics_per_day_5", "topics_per_day_8", "topics_per_day_9")) {
    r = TRUE
  } 
  if (df %in% c("topics_per_day_4", "topics_per_day_10")) {
    next
  }  
  arima_its(as.Date("2020-05-19"),
            get(df),
            pulse = p,
            step = s,
            ramp = r)
}

# October 2nd
for (df in dfs) {
  print(df)
  p = FALSE
  r = FALSE
  s = FALSE
  if (df %in% c("topics_per_day_7", "topics_per_day_9")) {
    p = TRUE
  } 
  if (df %in% c("topics_per_day_0", "topics_per_day_3", "topics_per_day_5", "topics_per_day_9", "topics_per_day_10")) {
    s = TRUE
  } 
  if (df %in% c("topics_per_day_1", "topics_per_day_3", "topics_per_day_6")) {
    r = TRUE
  } 
  if (df %in% c("topics_per_day_4", "topics_per_day_8")) {
    next
  }  
  arima_its(as.Date("2020-10-02"),
            get(df),
            pulse = p,
            step = s,
            ramp = r)
}

```

### Running Models - Combined per Topic
```{r}
for (df in dfs) {
#for (df in c("topics_per_day_3", "topics_per_day_8")) {
  dat_ts_loop <- ts(as.numeric(unlist(get(df)["posts_per_day"])), 
                   start = as.Date("2020-01-06"), #Hard coding since we know this is the consistent start date
                   frequency = 365)

  df_loop <- get(df)
  df_loop$pulse <- 0
  df_loop$step <- 0
  df_loop$ramp <- 0
  
  #January 20th
  if (df %in% c("topics_per_day_4")) {
    df_loop$pulse <- ifelse(df_loop$post_created_date == as.Date("2020-01-20"), 
                            1, 
                            df_loop$pulse)
  } 
  
  if (df %in% c("topics_per_day_2", "topics_per_day_3", "topics_per_day_5")) {
    df_loop$step <- ifelse(df_loop$post_created_date >= as.Date("2020-01-20") &
                             df_loop$post_created_date <= as.Date("2020-01-20")+14,
                           1,
                           df_loop$step)
  } 

  if (df %in% c("topics_per_day_3", "topics_per_day_7")) {
    df_loop$ramp <- ifelse(df_loop$post_created_date >= as.Date("2020-01-20") &
                             df_loop$post_created_date <= as.Date("2020-01-20")+14,
                           as.numeric(difftime(as.Date(df_loop$post_created_date),
                                               as.Date("2020-01-20"), 
                                               units = "days")),
                           df_loop$ramp)
  }
 
  #March 11th
  if (df %in% c("topics_per_day_2", "topics_per_day_3", "topics_per_day_7")) {
    df_loop$pulse <- ifelse(df_loop$post_created_date == as.Date("2020-03-11"), 
                            1, 
                            df_loop$pulse)
  } 
  
  if (df %in% c("topics_per_day_3", "topics_per_day_7")) {
    df_loop$step <- ifelse(df_loop$post_created_date >= as.Date("2020-03-11") &
                             df_loop$post_created_date <= as.Date("2020-03-11")+14,
                           1,
                           df_loop$step)
  } 

  if (df %in% c("topics_per_day_4", "topics_per_day_5", "topics_per_day_7")) {
    df_loop$ramp <- ifelse(df_loop$post_created_date >= as.Date("2020-03-11") &
                             df_loop$post_created_date <= as.Date("2020-03-11")+14,
                           as.numeric(difftime(as.Date(df_loop$post_created_date),
                                               as.Date("2020-03-11"), 
                                               units = "days")),
                           df_loop$ramp)
  }
 
  #May 19th
  if (df %in% c("topics_per_day_5")) {
    df_loop$pulse <- ifelse(df_loop$post_created_date == as.Date("2020-05-19"), 
                            1, 
                            df_loop$pulse)
  } 
  
  if (df %in% c("topics_per_day_4", "topics_per_day_7")) {
    df_loop$step <- ifelse(df_loop$post_created_date >= as.Date("2020-05-19") &
                             df_loop$post_created_date <= as.Date("2020-05-19")+14,
                           1,
                           df_loop$step)
  } 

  if (df %in% c("topics_per_day_2", "topics_per_day_3", "topics_per_day_6")) {
    df_loop$ramp <- ifelse(df_loop$post_created_date >= as.Date("2020-05-19") &
                             df_loop$post_created_date <= as.Date("2020-05-19")+14,
                           as.numeric(difftime(as.Date(df_loop$post_created_date),
                                               as.Date("2020-05-19"), 
                                               units = "days")),
                           df_loop$ramp)
  }

  #October 2nd
  if (df %in% c("topics_per_day_7")) {
    df_loop$pulse <- ifelse(df_loop$post_created_date == as.Date("2020-10-02"), 
                            1, 
                            df_loop$pulse)
  } 
  
  if (df %in% c("topics_per_day_3", "topics_per_day_7")) {
    df_loop$step <- ifelse(df_loop$post_created_date >= as.Date("2020-10-02") &
                             df_loop$post_created_date <= as.Date("2020-10-02")+14,
                           1,
                           df_loop$step)
  } 

  if (df %in% c("topics_per_day_2", "topics_per_day_3", "topics_per_day_4", "topics_per_day_5", "topics_per_day_6", "topics_per_day_7")) {
    df_loop$ramp <- ifelse(df_loop$post_created_date >= as.Date("2020-10-02") &
                             df_loop$post_created_date <= as.Date("2020-10-02")+14,
                           as.numeric(difftime(as.Date(df_loop$post_created_date),
                                               as.Date("2020-10-02"), 
                                               units = "days")),
                           df_loop$ramp)
  }

df_loop_transfer <- df_loop %>%
  mutate(jan_20_range = case_when(post_created_date >= as.Date("2020-01-20") - 14 & post_created_date <= as.Date("2020-01-20") + 14 ~ 1,
                                  TRUE ~ 0),
         mar_11_range = case_when(post_created_date >= as.Date("2020-03-11") - 14 & post_created_date <= as.Date("2020-03-11") + 14 ~ 1,
                                  TRUE ~ 0),
         may_19_range = case_when(post_created_date >= as.Date("2020-05-19") - 14 & post_created_date <= as.Date("2020-05-19") + 14 ~ 1,
                                  TRUE ~ 0),
         oct_02_range = case_when(post_created_date >= as.Date("2020-10-02") - 14 & post_created_date <= as.Date("2020-10-02") + 14 ~ 1,
                                  TRUE ~ 0),
         jan20_pulse = jan_20_range*pulse,
         jan20_step = jan_20_range*step,
         jan20_ramp = jan_20_range*ramp,
         mar11_pulse = mar_11_range*pulse,
         mar11_step = mar_11_range*step,
         mar11_ramp = mar_11_range*ramp,
         may19_pulse = may_19_range*pulse,
         may19_step = may_19_range*step,
         may19_ramp = may_19_range*ramp,
         oct02_pulse = oct_02_range*pulse,
         oct02_step = oct_02_range*step,
         oct02_ramp = oct_02_range*ramp) %>%
  ungroup() %>%
  select(jan20_pulse, jan20_step, jan20_ramp, mar11_pulse, mar11_step, mar11_ramp, may19_pulse, may19_step, may19_ramp, oct02_pulse, oct02_step, oct02_ramp) %>% 
  select(which(!colSums(., na.rm=TRUE) %in% 0))

  loop_model <- auto.arima(dat_ts_loop,
                         xreg = as.matrix(df_loop_transfer),
                         stepwise = FALSE,
                         max.order = 10)
  print(df)
  print(arimaorder(loop_model))
  print(loop_model$coef)
  print(confint(loop_model))
  print((1-pnorm(abs(loop_model$coef)/sqrt(diag(loop_model$var.coef))))*2)
  print("**********")
}

```
