---
title: "instagram arima"
author: "CCP"
date: "1/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries and Packages
```{r}
library(tidyverse)
library(data.table) #fread
library(janitor) #clean_names
library(zoo) #numeric date to date
library(astsa) #adf.test
library(forecast) #arima
library(magrittr) #%<>%
```

# Functions
## ADF Test
```{r}
arima_its_adf_test <- function(its_date, 
                      dat, 
                      post_or_interaction = "post") {
  first_date = as.Date(its_date) - 30
  last_date = as.Date(its_date) + 30
  
  dat_filtered <- dat %>%
      dplyr::filter(post_created_date >= first_date &
                    post_created_date <= last_date)
  
  date_seq <- seq.Date(from = as.Date(first_date),
                         length.out = nrow(dat_filtered),
                         by = 1)

  if (post_or_interaction == "post") {
      dat_ts <- ts(as.numeric(dat_filtered$posts_per_day), 
                              start = first_date,
                              frequency = 365)

  } else {
      dat_ts <- ts(as.numeric(dat_filtered$interactions_per_day), 
                                   start = first_date,
                                   frequency = 365)
  }
  
  print(adf.test(dat_ts)) #Stationary data if significant (we want stationary)
}
```

## Function: ARIMA- ITS
```{r}
## Note: If adf.test is not significant, that means data needs to be differenced and this function re-run with difference = TRUE. This function does not difference the data. 
arima_its <- function(its_date, 
                      dat, 
                      difference = FALSE,
                      pulse = FALSE,
                      step = FALSE,
                      ramp = FALSE,
                      post_or_interaction = "post") {
  print(difference)
  first_date = as.Date(its_date) - 30
  last_date = as.Date(its_date) + 30
  
  dat_filtered <- dat %>%
      dplyr::filter(post_created_date >= first_date &
                    post_created_date <= last_date)
  
  date_seq <- seq.Date(from = as.Date(first_date),
                         length.out = nrow(dat_filtered),
                         by = 1)

  if (post_or_interaction == "post") {
      dat_ts <- ts(as.numeric(dat_filtered$posts_per_day), 
                              start = first_date,
                              frequency = 365)

  } else {
      dat_ts <- ts(as.numeric(dat_filtered$interactions_per_day), 
                                   start = first_date,
                                   frequency = 365)
  }
  
  #print(adf.test(dat_ts)) #Stationary data if significant (we want stationary)

## Step Parameter
  transfer <- c()
  if (step == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    transfer <- cbind(transfer, dat_step)
  }

## Ramp Parameter
  if (ramp == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    dat_ramp <- append(rep(0,
                         length(which(dat_step == 0))),
                     seq(1,
                         length(which(dat_step == 1)),
                         1))
    transfer <- cbind(transfer, dat_ramp)
  }
## Pulse Parameter
  if (pulse == TRUE) {
    dat_pulse <- ifelse(date_seq == its_date, 1, 0)
    transfer <- cbind(transfer, dat_pulse)
  }

  if (difference == TRUE) {
    print("Running with differencing")
      model_func <- auto.arima(dat_ts,
                               d = 1, #Considers differencing data
                               xreg = transfer)
  } else {
    print("Running with no differencing")
      model_func <- auto.arima(dat_ts,
                               xreg = transfer)
  }

  #print(Box.test(model_func$residuals, 
  #         type = "Ljung-Box")) 

  print(summary(model_func))
  print(confint(model_func))
  print((1-pnorm(abs(model_func$coef)/sqrt(diag(model_func$var.coef))))*2)
}
```

# Data
```{r}
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/data")
obesity_instagram <- fread("220106_obesity_instagram.csv") %>%
  clean_names()
headaches_instagram <- fread("220106_health_control_instagram.csv") %>%
  clean_names()
clarinet_instagram <- fread("220106_non_health_control_instagram.csv") %>% 
  clean_names()
```

# Posts per Day
```{r}
obesity_count_per_day_instagram <- obesity_instagram %>%
  group_by(post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  mutate(data_set = "Obesity")

headaches_count_per_day_instagram <- headaches_instagram %>%
  group_by(post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  mutate(data_set = "Health Comparator")

clarinet_count_per_day_instagram <- clarinet_instagram %>%
  group_by(post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  mutate(data_set = "Non-Health Comparator")
```

## Checking for Differencing Need
```{r}
list_of_its_dates <- c(as.Date("2020-01-20"),
                       as.Date("2020-03-11"),
                       as.Date("2020-05-19"),
                       as.Date("2020-10-02"))

dfs_posts <- c("obesity_count_per_day_instagram", 
                      "headaches_count_per_day_instagram",
                      "clarinet_count_per_day_instagram")

for (d in list_of_its_dates) {
  print(as.Date(d))
  for (df in dfs_posts) {
    print(df)
    arima_its_adf_test(d, get(df))
  }
}
```

## Model Selection
- January 20th: Difference obesity
- March 11th: Difference non-health control
- May 19th: Difference health control
- October 2nd: No difference
```{r}
# No differencing (everything but January 20)
for (d in list_of_its_dates) {
  if (as.Date(d) == as.Date("2020-01-20")) {
    diff = TRUE
  } else {
    diff = FALSE
  }
  print(as.Date(d))
  print("pulse only")
  arima_its(d, obesity_count_per_day_instagram, pulse = TRUE,
            difference = diff)
  print("**********")
  
  print("step only")
  arima_its(d, obesity_count_per_day_instagram, step = TRUE,
            difference = diff)
  print("**********")
  
  print("ramp only")
  arima_its(d, obesity_count_per_day_instagram, ramp = TRUE,
            difference = diff)
  print("**********")
  
  print("pulse + step only")
  arima_its(d, obesity_count_per_day_instagram, 
            pulse = TRUE, 
            step = TRUE,
            difference = diff)
  print("**********")
  
  print("pulse + ramp only")
  arima_its(d, obesity_count_per_day_instagram, 
            pulse = TRUE, ramp = TRUE,
            difference = diff)
  print("**********")
  
  print("step + ramp only")
  arima_its(d, obesity_count_per_day_instagram, 
            step = TRUE, ramp = TRUE,
            difference = diff)
  print("**********")
  
  print("all")
  arima_its(d, obesity_count_per_day_instagram,
            pulse = TRUE, step = TRUE, ramp = TRUE,
            difference = diff)
  print("**********")
}
```

## Running Models
- January 20th: Difference obesity
- March 11th: Difference non-health control
- May 19th: Difference health control
- October 2nd: No difference
```{r}
# January 20th
for (df in dfs_posts) {
  print(df)
  if (df == "obesity_count_per_day_instagram") {
    arima_its(as.Date("2020-01-20"), get(df), 
              difference = TRUE, 
              pulse = TRUE)
  } else {
    arima_its(as.Date("2020-01-20"), get(df), 
              difference = FALSE, 
              pulse = TRUE)
  }
}

# March 11th
for (df in dfs_posts) {
  print(df)
  if (df == "clarinet_count_per_day_instagram") {
    arima_its(as.Date("2020-03-11"), get(df), 
              difference = TRUE, 
              step = TRUE)
  } else {
    arima_its(as.Date("2020-03-11"), get(df), 
              difference = FALSE, 
              step = TRUE)
  }
}

# May 19th
for (df in dfs_posts) {
  print(df)
  if (df == "headaches_count_per_day_instagram") {
    arima_its(as.Date("2020-05-19"), get(df),
              difference = TRUE,
              pulse = TRUE)
  } else {
    arima_its(as.Date("2020-05-19"), get(df),
              difference = FALSE, 
              pulse = TRUE)
  }
}

# October 2nd
for (df in dfs_posts) {
  print(df)
    arima_its(as.Date("2020-10-02"), get(df),
              difference = FALSE, 
              pulse = TRUE)
  }
```

# Interaction per Day
```{r}
obesity_instagram %<>%
  mutate(total_interactions_numeric = as.numeric(str_remove_all(total_interactions, " ")))

headaches_instagram %<>%
  mutate(total_interactions_numeric = as.numeric(str_remove_all(total_interactions, " ")))

clarinet_instagram %<>%
  mutate(total_interactions_numeric = as.numeric(str_remove_all(total_interactions, " ")))

obesity_interaction_per_day <- obesity_instagram %>%
  group_by(post_created_date) %>%
  summarise(interactions_per_day = sum(total_interactions_numeric, na.rm = TRUE)) %>%
  mutate(data_set = "Obesity")

headaches_interaction_per_day <- headaches_instagram %>%
  group_by(post_created_date) %>%
  summarise(interactions_per_day = sum(total_interactions_numeric, na.rm = TRUE)) %>%
  mutate(data_set = "Health Comparator")

clarinet_interaction_per_day <- clarinet_instagram %>%
  group_by(post_created_date) %>%
  summarise(interactions_per_day = sum(total_interactions_numeric, na.rm = TRUE)) %>%
  mutate(data_set = "Non-Health Comparator")
```

## Checking for Differencing Need
```{r}
list_of_its_dates <- c(as.Date("2020-01-20"),
                       as.Date("2020-03-11"),
                       as.Date("2020-05-19"),
                       as.Date("2020-10-02"))

dfs_posts <- c("obesity_interaction_per_day", 
                      "headaches_interaction_per_day",
                      "clarinet_interaction_per_day")

for (d in list_of_its_dates) {
  print(as.Date(d))
  for (df in dfs_posts) {
    print(df)
    arima_its_adf_test(d, get(df), post_or_interaction = "interactions")
  }
}
```

## Model Selection
- January 20th: Difference obesity and non-health control
- March 11th: Difference non-health control
- May 19th: Difference non-health control
- October 2nd: Difference non-health difference
```{r}
# No differencing (everything but January 20)
for (d in list_of_its_dates) {
  if (as.Date(d) == as.Date("2020-01-20")) {
    diff = TRUE
  } else {
    diff = FALSE
  }
  print(as.Date(d))
  print("pulse only")
  arima_its(d, obesity_interaction_per_day, pulse = TRUE,
            difference = diff, post_or_interaction = "interactions")
  print("**********")
  
  print("step only")
  arima_its(d, obesity_interaction_per_day, step = TRUE,
            difference = diff, post_or_interaction = "interactions")
  print("**********")
  
  print("ramp only")
  arima_its(d, obesity_interaction_per_day, ramp = TRUE,
            difference = diff, post_or_interaction = "interactions")
  print("**********")
  
  print("pulse + step only")
  arima_its(d, obesity_interaction_per_day, 
            pulse = TRUE, 
            step = TRUE,
            difference = diff, post_or_interaction = "interactions")
  print("**********")
  
  print("pulse + ramp only")
  arima_its(d, obesity_interaction_per_day, 
            pulse = TRUE, ramp = TRUE,
            difference = diff, post_or_interaction = "interactions")
  print("**********")
  
  print("step + ramp only")
  arima_its(d, obesity_interaction_per_day, 
            step = TRUE, ramp = TRUE,
            difference = diff, post_or_interaction = "interactions")
  print("**********")
  
  print("all")
  arima_its(d, obesity_interaction_per_day,
            pulse = TRUE, step = TRUE, ramp = TRUE,
            difference = diff, post_or_interaction = "interactions")
  print("**********")
}
```

## Running Models
- January 20th: Difference obesity and non-health control
- March 11th: Difference non-health control
- May 19th: Difference non-health control
- October 2nd: Difference non-health difference
```{r}
# January 20th
for (df in dfs_posts) {
  print(df)
  if (df != "headaches_interaction_per_day") {
    arima_its(as.Date("2020-01-20"), get(df), 
              difference = TRUE, post_or_interaction = "interactions", 
              step = TRUE)
  } else {
    arima_its(as.Date("2020-01-20"), get(df), 
              difference = FALSE, post_or_interaction = "interactions", 
              step = TRUE)
  }
}

# March 11th
for (df in dfs_posts) {
  print(df)
  if (df == "clarinet_interaction_per_day") {
    arima_its(as.Date("2020-03-11"), get(df), 
              difference = TRUE, post_or_interaction = "interactions", 
              pulse = TRUE)
  } else {
    arima_its(as.Date("2020-03-11"), get(df), 
              difference = FALSE, post_or_interaction = "interactions", 
              pulse = TRUE)
  }
}

# May 19th
for (df in dfs_posts) {
  print(df)
  if (df == "clarinet_interaction_per_day") {
    arima_its(as.Date("2020-05-19"), get(df),
              difference = TRUE, post_or_interaction = "interactions",
              pulse = TRUE, step = TRUE)
  } else {
    arima_its(as.Date("2020-05-19"), get(df),
              difference = FALSE, post_or_interaction = "interactions", 
              pulse = TRUE, step = TRUE)
  }
}

# October 2nd
for (df in dfs_posts) {
  print(df)
  if (df == "clarinet_interaction_per_day") {
    arima_its(as.Date("2020-10-02"), get(df),
              difference = TRUE, post_or_interaction = "interactions",
              pulse = TRUE)
  } else {
    arima_its(as.Date("2020-10-02"), get(df),
              difference = FALSE, post_or_interaction = "interactions", 
              pulse = TRUE)
  }
}
```


