---
title: "instagram arima"
author: "CCP"
date: "1/6/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries and Packages
```{r}
library(tidyverse)
library(data.table) #fread
library(janitor) #clean_names
library(zoo) #numeric date to date
library(aTSA) #adf.test
library(forecast) #arima
library(magrittr) #%<>%
```

# Functions
## ADF Test
```{r}
arima_its_adf_test <- function(its_date, 
                      dat, 
                      post_or_interaction = "post") {
  first_date = as.Date(its_date) - 14
  last_date = as.Date(its_date) + 14
  
  dat_filtered <- dat %>%
      dplyr::filter(post_created_date >= first_date &
                    post_created_date <= last_date)
  
  date_seq <- seq.Date(from = as.Date(first_date),
                         length.out = nrow(dat_filtered),
                         by = 1)

  if (post_or_interaction == "post") {
      dat_ts <- ts(as.numeric(dat_filtered$posts_per_day), 
                              start = first_date,
                              frequency = 365)

  } else {
      dat_ts <- ts(as.numeric(dat_filtered$interactions_per_day), 
                                   start = first_date,
                                   frequency = 365)
  }
  
  print(adf.test(dat_ts)) #Stationary data if significant (we want stationary)
}
```

## ARIMA- ITS
```{r}
## Note: If adf.test is not significant, that means data needs to be differenced and this function re-run with difference = TRUE. This function does not difference the data. 
arima_its <- function(its_date, 
                      dat, 
                      difference = NA,
                      pulse = FALSE,
                      step = FALSE,
                      ramp = FALSE,
                      post_or_interaction = "post") {
  print(difference)
  first_date = as.Date(its_date) - 14
  last_date = as.Date(its_date) + 14
  
  dat_filtered <- dat %>%
      dplyr::filter(post_created_date >= first_date &
                    post_created_date <= last_date)
  
  date_seq <- seq.Date(from = as.Date(first_date),
                         length.out = nrow(dat_filtered),
                         by = 1)

  if (post_or_interaction == "post") {
      dat_ts <- ts(as.numeric(dat_filtered$posts_per_day), 
                              start = first_date,
                              frequency = 365)

  } else {
      dat_ts <- ts(as.numeric(dat_filtered$interactions_per_day), 
                                   start = first_date,
                                   frequency = 365)
  }
  
  #print(adf.test(dat_ts)) #Stationary data if significant (we want stationary)

## Step Parameter
  transfer <- c()
  if (step == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    transfer <- cbind(transfer, dat_step)
  }

## Ramp Parameter
  if (ramp == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    dat_ramp <- append(rep(0,
                         length(which(dat_step == 0))),
                     seq(1,
                         length(which(dat_step == 1)),
                         1))
    transfer <- cbind(transfer, dat_ramp)
  }
## Pulse Parameter
  if (pulse == TRUE) {
    dat_pulse <- ifelse(date_seq == its_date, 1, 0)
    transfer <- cbind(transfer, dat_pulse)
  }

  if (!is.na(difference)) {
    print(paste0("Running with differencing of ", difference))
      model_func <- auto.arima(dat_ts,
                               d = difference, #Considers differencing data
                               xreg = transfer,
                               stepwise = FALSE,
                               max.order = 10)
  } else {
    print("Running with no differencing")
      model_func <- auto.arima(dat_ts,
                               xreg = transfer,
                               stepwise = FALSE,
                               max.order = 10)
  }

  #print(Box.test(model_func$residuals, 
  #         type = "Ljung-Box")) 

  print(summary(model_func))
  print(confint(model_func))
  print((1-pnorm(abs(model_func$coef)/sqrt(diag(model_func$var.coef))))*2)
}
```

## ARIMA-ITS - Fixed Parameters
```{r}
## Note: This function assumes that p,d, and q parameters have already been found in a prior step

arima_its_fixed_pq <- function(its_date, 
                      dat, 
                      difference = NA,
                      pulse = FALSE,
                      step = FALSE,
                      ramp = FALSE,
                      post_or_interaction = "post",
                      p = NA,
                      d = NA,
                      q = NA) {
  print(difference)
  first_date = as.Date(its_date) - 14
  last_date = as.Date(its_date) + 14
  
  dat_filtered <- dat %>%
      dplyr::filter(post_created_date >= first_date &
                    post_created_date <= last_date)
  
  date_seq <- seq.Date(from = as.Date(first_date),
                         length.out = nrow(dat_filtered),
                         by = 1)

  if (post_or_interaction == "post") {
      dat_ts <- ts(as.numeric(dat_filtered$posts_per_day), 
                              start = first_date,
                              frequency = 365)

  } else {
      dat_ts <- ts(as.numeric(dat_filtered$interactions_per_day), 
                                   start = first_date,
                                   frequency = 365)
  }
  
  #print(adf.test(dat_ts)) #Stationary data if significant (we want stationary)

## Step Parameter
  transfer <- c()
  if (step == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    transfer <- cbind(transfer, dat_step)
  }

## Ramp Parameter
  if (ramp == TRUE) {
    dat_step <- ifelse(date_seq >= its_date, 1, 0)
    dat_ramp <- append(rep(0,
                         length(which(dat_step == 0))),
                     seq(1,
                         length(which(dat_step == 1)),
                         1))
    transfer <- cbind(transfer, dat_ramp)
  }
## Pulse Parameter
  if (pulse == TRUE) {
    dat_pulse <- ifelse(date_seq == its_date, 1, 0)
    transfer <- cbind(transfer, dat_pulse)
  }

  if (!is.na(difference)) {
    print(paste0("Running with differencing of ", difference))
      model_func <- Arima(dat_ts,
                          order = c(p, difference, q),
                          xreg = transfer)
  } else {
    print("Running with no differencing")
      model_func <- Arima(dat_ts,
                          order = c(p, 0, q),
                          xreg = transfer)
  }

  #print(Box.test(model_func$residuals, 
  #         type = "Ljung-Box")) 

  print(summary(model_func))
  print(confint(model_func))
  print((1-pnorm(abs(model_func$coef)/sqrt(diag(model_func$var.coef))))*2)
}

```

# Data
```{r}
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/data")
obesity_instagram <- fread("220106_obesity_instagram.csv") %>%
  clean_names()
headaches_instagram <- fread("220106_health_control_instagram.csv") %>%
  clean_names()
clarinet_instagram <- fread("220106_non_health_control_instagram.csv") %>% 
  clean_names()
```

# Posts per Day
```{r}
obesity_count_per_day_instagram <- obesity_instagram %>%
  group_by(post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  mutate(data_set = "Obesity")

headaches_count_per_day_instagram <- headaches_instagram %>%
  group_by(post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  mutate(data_set = "Health Comparator")

clarinet_count_per_day_instagram <- clarinet_instagram %>%
  group_by(post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  mutate(data_set = "Non-Health Comparator")

all_count_per_day <- rbind(obesity_count_per_day_instagram, headaches_count_per_day_instagram, clarinet_count_per_day_instagram)

```

## Checking for Differencing Need
```{r}
list_of_its_dates <- c(as.Date("2020-01-20"),
                       as.Date("2020-03-11"),
                       as.Date("2020-05-19"),
                       as.Date("2020-10-02"))

dfs_posts <- c("obesity_count_per_day_instagram", 
                      "headaches_count_per_day_instagram",
                      "clarinet_count_per_day_instagram")

for (d in list_of_its_dates) {
  print(as.Date(d))
  for (df in dfs_posts) {
    print(df)
    arima_its_adf_test(d, get(df))
  }
}
```

## Model Selection
- March 11th: Lag 2
- Everything Else: Lag 0
```{r}
# Lag 2 March 11th, everything else 0 
for (d in list_of_its_dates) {
  if (as.Date(d) == as.Date("2020-03-11")) {
    diff = 2
  } else {
    diff = NA
  }
  print(as.Date(d))
  print("pulse only")
  arima_its(d, obesity_count_per_day_instagram, pulse = TRUE,
            difference = diff)
  print("**********")
  
  print("step only")
  arima_its(d, obesity_count_per_day_instagram, step = TRUE,
            difference = diff)
  print("**********")
  
  print("ramp only")
  arima_its(d, obesity_count_per_day_instagram, ramp = TRUE,
            difference = diff)
  print("**********")
  
  print("pulse + step only")
  arima_its(d, obesity_count_per_day_instagram, 
            pulse = TRUE, 
            step = TRUE,
            difference = diff)
  print("**********")
  
  print("pulse + ramp only")
  arima_its(d, obesity_count_per_day_instagram, 
            pulse = TRUE, ramp = TRUE,
            difference = diff)
  print("**********")
  
  print("step + ramp only")
  arima_its(d, obesity_count_per_day_instagram, 
            step = TRUE, ramp = TRUE,
            difference = diff)
  print("**********")
  
  print("all")
  arima_its(d, obesity_count_per_day_instagram,
            pulse = TRUE, step = TRUE, ramp = TRUE,
            difference = diff)
  print("**********")
}
```

## Running Models
- January 20th: No Differene
- March 11th: Lag 2 Obesity
- May 19th: No Difference
- October 2nd: No Difference
```{r}
# January 20th
for (df in dfs_posts) {
  print(df)
  arima_its(as.Date("2020-01-20"),
            get(df),
            pulse = TRUE)
}

# March 11th
for (df in dfs_posts) {
  print(df)
  if (df == "obesity_count_per_day_instagram") {
    arima_its(as.Date("2020-03-11"),
              get(df), 
              difference = 2, 
              pulse = TRUE)
  } else {
    arima_its(as.Date("2020-03-11"),
              get(df), 
              pulse = TRUE)
  }
}

# May 19th
for (df in dfs_posts) {
  print(df)
  arima_its(as.Date("2020-05-19"),
            get(df),
            pulse = TRUE)
}

# October 2nd
for (df in dfs_posts) {
  print(df)
    arima_its(as.Date("2020-10-02"),
              get(df),
              pulse = TRUE)
}
```

## Repeat with fixed p,q
January 20th: p = 0, q = 1
March 11th: p = 4, q = 0
May 19th: p = 0, q = 0
October 2nd: p = 3, q = 0
```{r}
# January 20th
for (df in dfs_posts) {
  print(df)
  arima_its_fixed_pq(as.Date("2020-01-20"),
            get(df),
            pulse = TRUE,
            p = 0, q = 1)
}

# March 11th
for (df in dfs_posts) {
  print(df)
  if (df == "obesity_count_per_day_instagram") {
    arima_its_fixed_pq(as.Date("2020-03-11"),
              get(df), 
              difference = 2, 
              pulse = TRUE,
              p = 4, q = 0)
  } else {
    arima_its_fixed_pq(as.Date("2020-03-11"),
              get(df), 
              pulse = TRUE,
              p = 4, q = 0)
  }
}

# May 19th
for (df in dfs_posts) {
  print(df)
  arima_its_fixed_pq(as.Date("2020-05-19"),
            get(df),
            pulse = TRUE,
            p = 0, q = 0)
}

# October 2nd
for (df in dfs_posts) {
  print(df)
    arima_its_fixed_pq(as.Date("2020-10-02"),
              get(df),
              pulse = TRUE,
              p = 3, q = 0)
}
```

# Interaction per Day
```{r}
obesity_instagram %<>%
  mutate(total_interactions_numeric = as.numeric(str_remove_all(total_interactions, " ")))

headaches_instagram %<>%
  mutate(total_interactions_numeric = as.numeric(str_remove_all(total_interactions, " ")))

clarinet_instagram %<>%
  mutate(total_interactions_numeric = as.numeric(str_remove_all(total_interactions, " ")))

obesity_interaction_per_day <- obesity_instagram %>%
  group_by(post_created_date) %>%
  summarise(interactions_per_day = sum(total_interactions_numeric, na.rm = TRUE)) %>%
  mutate(data_set = "Obesity")

headaches_interaction_per_day <- headaches_instagram %>%
  group_by(post_created_date) %>%
  summarise(interactions_per_day = sum(total_interactions_numeric, na.rm = TRUE)) %>%
  mutate(data_set = "Health Comparator")

clarinet_interaction_per_day <- clarinet_instagram %>%
  group_by(post_created_date) %>%
  summarise(interactions_per_day = sum(total_interactions_numeric, na.rm = TRUE)) %>%
  mutate(data_set = "Non-Health Comparator")

all_interactions_per_day <- rbind(obesity_interaction_per_day, headaches_interaction_per_day, clarinet_interaction_per_day)

```

## Checking for Differencing Need
```{r}
list_of_its_dates <- c(as.Date("2020-01-20"),
                       as.Date("2020-03-11"),
                       as.Date("2020-05-19"),
                       as.Date("2020-10-02"))

dfs_posts <- c("obesity_interaction_per_day", 
                      "headaches_interaction_per_day",
                      "clarinet_interaction_per_day")

for (d in list_of_its_dates) {
  print(as.Date(d))
  for (df in dfs_posts) {
    print(df)
    arima_its_adf_test(d, get(df), post_or_interaction = "interactions")
  }
}
```

## Model Selection
No Differencing
```{r}
# No differencing (everything but January 20)
for (d in list_of_its_dates) {
  print(as.Date(d))
  print("pulse only")
  arima_its(d,
            obesity_interaction_per_day,
            pulse = TRUE,
            post_or_interaction = "interactions")
  print("**********")
  
  print("step only")
  arima_its(d, obesity_interaction_per_day, step = TRUE, post_or_interaction = "interactions")
  print("**********")
  
  print("ramp only")
  arima_its(d, obesity_interaction_per_day, ramp = TRUE, post_or_interaction = "interactions")
  print("**********")
  
  print("pulse + step only")
  arima_its(d, obesity_interaction_per_day, 
            pulse = TRUE, 
            step = TRUE, post_or_interaction = "interactions")
  print("**********")
  
  print("pulse + ramp only")
  arima_its(d, obesity_interaction_per_day, 
            pulse = TRUE, ramp = TRUE,
 post_or_interaction = "interactions")
  print("**********")
  
  print("step + ramp only")
  arima_its(d, obesity_interaction_per_day, 
            step = TRUE, ramp = TRUE,
 post_or_interaction = "interactions")
  print("**********")
  
  print("all")
  arima_its(d, obesity_interaction_per_day,
            pulse = TRUE, step = TRUE, ramp = TRUE,
 post_or_interaction = "interactions")
  print("**********")
}
```

## Running Models
No differencing
```{r}
# January 20th
for (df in dfs_posts) {
  print(df)
    arima_its(as.Date("2020-01-20"),
              get(df),
              post_or_interaction = "interactions", 
              ramp = TRUE)
}

# March 11th
for (df in dfs_posts) {
  print(df)
  arima_its(as.Date("2020-03-11"), 
            get(df), 
            post_or_interaction = "interactions", 
            ramp = TRUE)
}

# May 19th
for (df in dfs_posts) {
  print(df)
  arima_its(as.Date("2020-05-19"), 
            get(df),
            post_or_interaction = "interactions", 
            pulse = TRUE, step = TRUE)
}

# October 2nd
for (df in dfs_posts) {
  print(df)
    arima_its(as.Date("2020-10-02"), 
              get(df),
              post_or_interaction = "interactions", 
              pulse = TRUE)
}
```

## Repeating with fixed p q
January 20th: p = 0, q = 0
March 11th: p = 0, q = 0
May 19th: p = 0, q = 0
October 2nd: p = 2, q = 0
No differencing
```{r}
# January 20th
for (df in dfs_posts) {
  print(df)
    arima_its_fixed_pq(as.Date("2020-01-20"),
              get(df),
              post_or_interaction = "interactions", 
              ramp = TRUE,
              p = 0, q = 0)
}

# March 11th
for (df in dfs_posts) {
  print(df)
  arima_its_fixed_pq(as.Date("2020-03-11"), 
            get(df), 
            post_or_interaction = "interactions", 
            ramp = TRUE,
            p = 0, q = 0)
}

# May 19th
for (df in dfs_posts) {
  print(df)
  arima_its_fixed_pq(as.Date("2020-05-19"), 
            get(df),
            post_or_interaction = "interactions", 
            pulse = TRUE, step = TRUE,
            p = 0, q = 0)
}

# October 2nd
for (df in dfs_posts) {
  print(df)
    arima_its_fixed_pq(as.Date("2020-10-02"), 
              get(df),
              post_or_interaction = "interactions", 
              pulse = TRUE,
              p = 2, q = 0)
}
```

# Combining Into One Model
## Posts
### Obesity Data
```{r}
all_count_per_day_restricted <- all_count_per_day %>%
  filter(post_created_date >= as.Date("2020-01-20") - 14 &
           post_created_date <= as.Date("2020-10-02") + 14) %>%
  mutate(pulse = case_when(
    post_created_date %in% c(as.Date("2020-01-20"), ("2020-03-11"), as.Date("2020-05-19"), as.Date("2020-10-02")) ~ 1,
    TRUE ~ 0),
    is_obesity = case_when(
      data_set == "Obesity" ~ 1,
      TRUE ~ 0),
    is_health_control = case_when(
      data_set == "Health Comparator" ~ 1,
      TRUE ~ 0),
    is_non_health_control = case_when(
      data_set == "Non-Health Comparator" ~ 1,
      TRUE ~ 0))

obesity_count_per_day_restricted <- all_count_per_day_restricted %>%
  filter(is_obesity == 1)

obesity_dat_ts <- ts(as.numeric(obesity_count_per_day_restricted$posts_per_day), start = min(obesity_count_per_day_restricted$post_created_date),
                     frequency = 365)

obesity_count_per_day_restricted_transfer <- obesity_count_per_day_restricted %>%
  mutate(jan_20_range = case_when(post_created_date >= as.Date("2020-01-20") - 14 & post_created_date <= as.Date("2020-01-20") + 14 ~ 1,
                                  TRUE ~ 0),
         mar_11_range = case_when(post_created_date >= as.Date("2020-03-11") - 14 & post_created_date <= as.Date("2020-03-11") + 14 ~ 1,
                                  TRUE ~ 0),
         may_19_range = case_when(post_created_date >= as.Date("2020-05-19") - 14 & post_created_date <= as.Date("2020-05-19") + 14 ~ 1,
                                  TRUE ~ 0),
         oct_02_range = case_when(post_created_date >= as.Date("2020-10-02") - 14 & post_created_date <= as.Date("2020-10-02") + 14 ~ 1,
                                  TRUE ~ 0),
         jan20_obesity_pulse = jan_20_range*pulse,
         mar11_obesity_pulse = mar_11_range*pulse,
         may19_obesity_pulse = may_19_range*pulse,
         oct02_obesity_pulse = oct_02_range*pulse) %>%
  select(jan20_obesity_pulse, mar11_obesity_pulse, may19_obesity_pulse, oct02_obesity_pulse)

obesity_full_model <- auto.arima(obesity_dat_ts,
                         xreg = as.matrix(obesity_count_per_day_restricted_transfer),
                         stepwise = FALSE,
                         trace = TRUE,
                         max.order = 10)
summary(obesity_full_model)
print(confint(obesity_full_model))
print((1-pnorm(abs(obesity_full_model$coef)/sqrt(diag(obesity_full_model$var.coef))))*2)
```

### Health Control
```{r}
health_count_per_day_restricted <- all_count_per_day_restricted %>%
  filter(is_health_control == 1)

health_dat_ts <- ts(as.numeric(health_count_per_day_restricted$posts_per_day), start = min(health_count_per_day_restricted$post_created_date),
                     frequency = 365)

health_count_per_day_restricted_transfer <- health_count_per_day_restricted %>%
  mutate(jan_20_range = case_when(post_created_date >= as.Date("2020-01-20") - 14 & post_created_date <= as.Date("2020-01-20") + 14 ~ 1,
                                  TRUE ~ 0),
         mar_11_range = case_when(post_created_date >= as.Date("2020-03-11") - 14 & post_created_date <= as.Date("2020-03-11") + 14 ~ 1,
                                  TRUE ~ 0),
         may_19_range = case_when(post_created_date >= as.Date("2020-05-19") - 14 & post_created_date <= as.Date("2020-05-19") + 14 ~ 1,
                                  TRUE ~ 0),
         oct_02_range = case_when(post_created_date >= as.Date("2020-10-02") - 14 & post_created_date <= as.Date("2020-10-02") + 14 ~ 1,
                                  TRUE ~ 0),
         jan20_pulse = jan_20_range*pulse,
         mar11_pulse = mar_11_range*pulse,
         may19_pulse = may_19_range*pulse,
         oct02_pulse = oct_02_range*pulse) %>%
  select(jan20_pulse, mar11_pulse, may19_pulse, oct02_pulse)

health_full_model <- auto.arima(health_dat_ts,
                         xreg = as.matrix(health_count_per_day_restricted_transfer),
                         stepwise = FALSE,
                         trace = TRUE,
                         max.order = 10)
summary(health_full_model)
print(confint(health_full_model))
print((1-pnorm(abs(health_full_model$coef)/sqrt(diag(health_full_model$var.coef))))*2)
```

### Non-Health Control
```{r}
nonhealth_count_per_day_restricted <- all_count_per_day_restricted %>%
  filter(is_non_health_control == 1)

nonhealth_dat_ts <- ts(as.numeric(nonhealth_count_per_day_restricted$posts_per_day), start = min(nonhealth_count_per_day_restricted$post_created_date),
                     frequency = 365)

nonhealth_count_per_day_restricted_transfer <- nonhealth_count_per_day_restricted %>%
  mutate(jan_20_range = case_when(post_created_date >= as.Date("2020-01-20") - 14 & post_created_date <= as.Date("2020-01-20") + 14 ~ 1,
                                  TRUE ~ 0),
         mar_11_range = case_when(post_created_date >= as.Date("2020-03-11") - 14 & post_created_date <= as.Date("2020-03-11") + 14 ~ 1,
                                  TRUE ~ 0),
         may_19_range = case_when(post_created_date >= as.Date("2020-05-19") - 14 & post_created_date <= as.Date("2020-05-19") + 14 ~ 1,
                                  TRUE ~ 0),
         oct_02_range = case_when(post_created_date >= as.Date("2020-10-02") - 14 & post_created_date <= as.Date("2020-10-02") + 14 ~ 1,
                                  TRUE ~ 0),
         jan20_pulse = jan_20_range*pulse,
         mar11_pulse = mar_11_range*pulse,
         may19_pulse = may_19_range*pulse,
         oct02_pulse = oct_02_range*pulse) %>%
  select(jan20_pulse, mar11_pulse, may19_pulse, oct02_pulse)

nonhealth_full_model <- auto.arima(nonhealth_dat_ts,
                         xreg = as.matrix(nonhealth_count_per_day_restricted_transfer),
                         stepwise = FALSE,
                         trace = TRUE,
                         max.order = 10)
summary(nonhealth_full_model)
print(confint(nonhealth_full_model))
print((1-pnorm(abs(nonhealth_full_model$coef)/sqrt(diag(nonhealth_full_model$var.coef))))*2)
```

## Interactions
Jan 20 - Ramp
March 11 - Ramp
May 19 - Pulse Step
October 2 - Pulse
### Obesity Data
```{r}
all_int_per_day_restricted <- all_interactions_per_day %>%
  filter(post_created_date >= as.Date("2020-01-20") - 14 &
           post_created_date <= as.Date("2020-10-02") + 14) %>%
  mutate(pulse = case_when(
    post_created_date %in% c(as.Date("2020-05-19"), as.Date("2020-10-02")) ~ 1,
    TRUE ~ 0),
    
    step = case_when(
      (post_created_date >= as.Date("2020-05-19") &
        post_created_date <= as.Date("2020-05-19") + 14) ~ 1,
      TRUE ~ 0),
    
    ramp = case_when(
      post_created_date >= as.Date("2020-01-20") &
        post_created_date <= as.Date("2020-01-20") + 14 ~ as.numeric(difftime(as.Date(post_created_date), as.Date("2020-01-20"), units = "days")),
      post_created_date >= as.Date("2020-03-11") &
        post_created_date <= as.Date("2020-03-11") + 14 ~ as.numeric(difftime(as.Date(post_created_date), as.Date("2020-03-11"), units = "days")),

      TRUE ~ 0),
    
    is_obesity = case_when(
      data_set == "Obesity" ~ 1,
      TRUE ~ 0),
    is_health_control = case_when(
      data_set == "Health Comparator" ~ 1,
      TRUE ~ 0),
    is_non_health_control = case_when(
      data_set == "Non-Health Comparator" ~ 1,
      TRUE ~ 0))

obesity_int_per_day_restricted <- all_int_per_day_restricted %>%
  filter(is_obesity == 1)

obesity_dat_ts <- ts(as.numeric(obesity_int_per_day_restricted$interactions_per_day), start = min(obesity_int_per_day_restricted$post_created_date),
                     frequency = 365)

obesity_in_per_day_restricted_transfer <- obesity_int_per_day_restricted %>%
  mutate(jan_20_range = case_when(post_created_date >= as.Date("2020-01-20") - 14 & post_created_date <= as.Date("2020-01-20") + 14 ~ 1,
                                  TRUE ~ 0),
         mar_11_range = case_when(post_created_date >= as.Date("2020-03-11") - 14 & post_created_date <= as.Date("2020-03-11") + 14 ~ 1,
                                  TRUE ~ 0),
         may_19_range = case_when(post_created_date >= as.Date("2020-05-19") - 14 & post_created_date <= as.Date("2020-05-19") + 14 ~ 1,
                                  TRUE ~ 0),
         oct_02_range = case_when(post_created_date >= as.Date("2020-10-02") - 14 & post_created_date <= as.Date("2020-10-02") + 14 ~ 1,
                                  TRUE ~ 0),
         jan20_ramp = jan_20_range*ramp,
         mar11_ramp = mar_11_range*ramp,
         may19_pulse = may_19_range*pulse,
         may19_step = may_19_range*step,
         oct02_pulse = oct_02_range*pulse) %>%
  select(jan20_ramp, mar11_ramp, may19_pulse, may19_step, oct02_pulse)

obesity_full_model <- auto.arima(obesity_dat_ts,
                         xreg = as.matrix(obesity_in_per_day_restricted_transfer),
                         stepwise = FALSE,
                         trace = TRUE,
                         max.order = 10)
summary(obesity_full_model)
print(confint(obesity_full_model))
print((1-pnorm(abs(obesity_full_model$coef)/sqrt(diag(obesity_full_model$var.coef))))*2)
```

### Health Control
```{r}
health_int_per_day_restricted <- all_int_per_day_restricted %>%
  filter(is_health_control == 1)

health_dat_ts <- ts(as.numeric(health_int_per_day_restricted$interactions_per_day), start = min(health_int_per_day_restricted$post_created_date),
                     frequency = 365)

health_int_per_day_restricted_transfer <- health_int_per_day_restricted %>%
  mutate(jan_20_range = case_when(post_created_date >= as.Date("2020-01-20") - 14 & post_created_date <= as.Date("2020-01-20") + 14 ~ 1,
                                  TRUE ~ 0),
         mar_11_range = case_when(post_created_date >= as.Date("2020-03-11") - 14 & post_created_date <= as.Date("2020-03-11") + 14 ~ 1,
                                  TRUE ~ 0),
         may_19_range = case_when(post_created_date >= as.Date("2020-05-19") - 14 & post_created_date <= as.Date("2020-05-19") + 14 ~ 1,
                                  TRUE ~ 0),
         oct_02_range = case_when(post_created_date >= as.Date("2020-10-02") - 14 & post_created_date <= as.Date("2020-10-02") + 14 ~ 1,
                                  TRUE ~ 0),
         jan20_ramp = jan_20_range*ramp,
         mar11_ramp = mar_11_range*ramp,
         may19_pulse = may_19_range*pulse,
         may19_step = may_19_range*step,
         oct02_pulse = oct_02_range*pulse) %>%
  select(jan20_ramp, mar11_ramp, may19_pulse, may19_step, oct02_pulse)

health_full_model <- auto.arima(health_dat_ts,
                         xreg = as.matrix(health_int_per_day_restricted_transfer),
                         stepwise = FALSE,
                         trace = TRUE,
                         max.order = 10)
summary(health_full_model)
print(confint(health_full_model))
print((1-pnorm(abs(health_full_model$coef)/sqrt(diag(health_full_model$var.coef))))*2)
```

### Non-Health Control
```{r}
nonhealth_int_per_day_restricted <- all_int_per_day_restricted %>%
  filter(is_non_health_control == 1)

nonhealth_dat_ts <- ts(as.numeric(nonhealth_int_per_day_restricted$interactions_per_day), start = min(nonhealth_int_per_day_restricted$post_created_date),
                     frequency = 365)

nonhealth_int_per_day_restricted_transfer <- nonhealth_int_per_day_restricted %>%
  mutate(jan_20_range = case_when(post_created_date >= as.Date("2020-01-20") - 14 & post_created_date <= as.Date("2020-01-20") + 14 ~ 1,
                                  TRUE ~ 0),
         mar_11_range = case_when(post_created_date >= as.Date("2020-03-11") - 14 & post_created_date <= as.Date("2020-03-11") + 14 ~ 1,
                                  TRUE ~ 0),
         may_19_range = case_when(post_created_date >= as.Date("2020-05-19") - 14 & post_created_date <= as.Date("2020-05-19") + 14 ~ 1,
                                  TRUE ~ 0),
         oct_02_range = case_when(post_created_date >= as.Date("2020-10-02") - 14 & post_created_date <= as.Date("2020-10-02") + 14 ~ 1,
                                  TRUE ~ 0),
         jan20_ramp = jan_20_range*ramp,
         mar11_ramp = mar_11_range*ramp,
         may19_pulse = may_19_range*pulse,
         may19_step = may_19_range*step,
         oct02_pulse = oct_02_range*pulse) %>%
  select(jan20_ramp, mar11_ramp, may19_pulse, may19_step, oct02_pulse)

nonhealth_full_model <- auto.arima(nonhealth_dat_ts,
                         xreg = as.matrix(nonhealth_int_per_day_restricted_transfer),
                         stepwise = FALSE,
                         trace = TRUE,
                         max.order = 10)
summary(nonhealth_full_model)
print(confint(nonhealth_full_model))
print((1-pnorm(abs(nonhealth_full_model$coef)/sqrt(diag(nonhealth_full_model$var.coef))))*2)
```


