---
title: "analysis"
author: "CCP"
date: "12/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bring in Libraries and Packages
```{r}
library(tidyverse)
library(data.table)
library(janitor)
library(magrittr)
library(ggsci)
library(CausalImpact)
library(reshape2)
```

# Bring in Data
```{r}
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/data")
obesity_1 <- fread("210526_facebook_obesity_1.csv")
obesity_2 <- fread("210526_facebook_obesity_2.csv")
obesity <- rbind(obesity_1, obesity_2) %>%
  clean_names()
rm(obesity_1, obesity_2)

headaches_1 <- fread("210627_headaches_1.csv")
headaches_2 <- fread("210627_headaches_2.csv")
headaches_3 <- fread("210627_headaches_3.csv")
headaches <- rbind(headaches_1, headaches_2, headaches_3) %>%
  clean_names()
rm(headaches_1, headaches_2, headaches_3)

clarinet <- fread("211104_facebook_clarinet_comparator.csv")
clarinet %<>%
  clean_names()
```

# Posts per Day
```{r}
obesity_count_per_day <- obesity %>%
  group_by(post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  mutate(data_set = "Obesity")

headaches_count_per_day <- headaches %>%
  group_by(post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  mutate(data_set = "Health Comparator")

clarinet_count_per_day <- clarinet %>%
  group_by(post_created_date) %>%
  summarise(posts_per_day = n()) %>%
  mutate(data_set = "Non-Health Comparator")

all_count_per_day <- rbind(obesity_count_per_day, headaches_count_per_day, clarinet_count_per_day)

all_count_per_day %>%
  mutate(data_set = factor(data_set, 
                           levels = c("Obesity",
                                      "Health Comparator",
                                      "Non-Health Comparator"))) %>%
  ggplot(aes(x = post_created_date,
             y = posts_per_day,
             color = data_set)) +
  geom_point() +
  geom_vline(xintercept = as.Date("2020-01-20"),
             linetype = "dashed") + 
  geom_vline(xintercept = as.Date("2020-03-11"),
             linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-05-19"),
             linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-10-20"),
             linetype = "dashed") +
  theme_classic() +
  scale_color_aaas() + 
  labs(title = "Temporal Variations in Obesity-Related Content on Facebook\nRelative to Comparators",
       x = "Date (Year-Month)",
       y = "Posts per Day",
       color = "Data Set") +
  theme(legend.position = "bottom")
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/figures")
ggsave("211214_change_in_posts_over_time_facebook.tiff", 
       width = 7.25,
       height = 4.51)
```

# BSTSM for Obesity vs. Health Comparator - # Posts
## January 20th, 2020 (First US Case)
```{r}
headaches_count_per_day <- rbind(headaches_count_per_day,
                                 c("2020-01-01", 0, "Health Comparator"))

headaches_count_per_day %<>%
  arrange(post_created_date)

obesity_headaches_count_per_day_date_restricted <- as.data.frame(cbind(filter(obesity_count_per_day,
                                                                post_created_date >= as.Date("2019-12-20") &
                                                                  post_created_date <= as.Date("2020-02-21"))$posts_per_day,
                                                         filter(headaches_count_per_day,
                                                                post_created_date >= as.Date("2019-12-20") &
                                                                  post_created_date <= as.Date("2020-02-21"))$posts_per_day))
                                                         
colnames(obesity_headaches_count_per_day_date_restricted) <- c("y", "x1")
obesity_headaches_count_per_day_date_restricted$y <- as.numeric(obesity_headaches_count_per_day_date_restricted$y)
obesity_headaches_count_per_day_date_restricted$x1 <- as.numeric(obesity_headaches_count_per_day_date_restricted$x1)

dat <- zoo(obesity_headaches_count_per_day_date_restricted,
           seq.Date(as.Date("2019-12-20"),
                    as.Date("2020-02-21"),
                    "day"))

pre_period <- as.Date(c("2019-12-20", "2020-01-20"))
post_period <- as.Date(c("2020-01-21", "2020-02-21"))
impact <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact)
summary(impact) #No difference after Jan. 20
```

## March 11, 2020 (WHO Pandemic)
```{r}
obesity_headaches_count_per_day_date_restricted_who <- as.data.frame(cbind(filter(obesity_count_per_day,
                                                                post_created_date >= as.Date("2020-02-11") &
                                                                  post_created_date <= as.Date("2020-04-12"))$posts_per_day,
                                                         filter(headaches_count_per_day,
                                                                post_created_date >= as.Date("2020-02-11") &
                                                                  post_created_date <= as.Date("2020-04-12"))$posts_per_day))
                                                         
colnames(obesity_headaches_count_per_day_date_restricted_who) <- c("y", "x1")
obesity_headaches_count_per_day_date_restricted_who$y <- as.numeric(obesity_headaches_count_per_day_date_restricted_who$y)
obesity_headaches_count_per_day_date_restricted_who$x1 <- as.numeric(obesity_headaches_count_per_day_date_restricted_who$x1)

dat <- zoo(obesity_headaches_count_per_day_date_restricted_who,
           seq.Date(as.Date("2020-02-11"),
                    as.Date("2020-04-12"),
                    "day"))

pre_period <- as.Date(c("2020-02-11", "2020-03-11"))
post_period <- as.Date(c("2020-03-12", "2020-04-12"))
impact_who <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_who)
summary(impact_who) #No significant difference
```

## May 19th, 2020 (Obesity linked with COVID-19)
```{r}
obesity_headaches_count_per_day_date_restricted_obesity_linked <- as.data.frame(cbind(filter(obesity_count_per_day,
                                                                post_created_date >= as.Date("2020-04-19") &
                                                                  post_created_date <= as.Date("2020-06-20"))$posts_per_day,
                                                         filter(headaches_count_per_day,
                                                                post_created_date >= as.Date("2020-04-19") &
                                                                  post_created_date <= as.Date("2020-06-20"))$posts_per_day))
                                                         
colnames(obesity_headaches_count_per_day_date_restricted_obesity_linked) <- c("y", "x1")
obesity_headaches_count_per_day_date_restricted_obesity_linked$y <- as.numeric(obesity_headaches_count_per_day_date_restricted_obesity_linked$y)
obesity_headaches_count_per_day_date_restricted_obesity_linked$x1 <- as.numeric(obesity_headaches_count_per_day_date_restricted_obesity_linked$x1)

dat <- zoo(obesity_headaches_count_per_day_date_restricted_obesity_linked,
           seq.Date(as.Date("2020-04-19"),
                    as.Date("2020-06-20"),
                    "day"))

pre_period <- as.Date(c("2020-04-19", "2020-05-19"))
post_period <- as.Date(c("2020-05-20", "2020-06-20"))
impact_obesity_linked <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_obesity_linked)
summary(impact_obesity_linked) #No significant difference after obesity linked
```

## October 2, 2020 (Trump gets COVID-19)
```{r}
headaches_count_per_day <- rbind(headaches_count_per_day,
                                 c("2020-11-01", 0, "Health Comparator"))

headaches_count_per_day %<>%
  arrange(post_created_date)

obesity_headaches_count_per_day_date_restricted_trump <- as.data.frame(cbind(filter(obesity_count_per_day,
                                                                post_created_date >= as.Date("2020-09-02") &
                                                                  post_created_date <= as.Date("2020-11-03"))$posts_per_day,
                                                         filter(headaches_count_per_day,
                                                                post_created_date >= as.Date("2020-09-02") &
                                                                  post_created_date <= as.Date("2020-11-03"))$posts_per_day))
                                                         
colnames(obesity_headaches_count_per_day_date_restricted_trump) <- c("y", "x1")
obesity_headaches_count_per_day_date_restricted_trump$y <- as.numeric(obesity_headaches_count_per_day_date_restricted_trump$y)
obesity_headaches_count_per_day_date_restricted_trump$x1 <- as.numeric(obesity_headaches_count_per_day_date_restricted_trump$x1)

dat <- zoo(obesity_headaches_count_per_day_date_restricted_trump,
           seq.Date(as.Date("2020-09-02"),
                    as.Date("2020-11-03"),
                    "day"))

pre_period <- as.Date(c("2020-09-02", "2020-10-02"))
post_period <- as.Date(c("2020-10-03", "2020-11-03"))
impact_trump <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_trump)
summary(impact_trump) #No significant difference after Trump gets COVID-19 
```

# BSTSM for Obesity vs. Non-Health Comparator - # Posts
## January 20th, 2020 (First US Case)
```{r}
obesity_clarinet_count_per_day_date_restricted <- as.data.frame(cbind(filter(obesity_count_per_day,
                                                                post_created_date >= as.Date("2019-12-20") &
                                                                  post_created_date <= as.Date("2020-02-21"))$posts_per_day,
                                                         filter(clarinet_count_per_day,
                                                                post_created_date >= as.Date("2019-12-20") &
                                                                  post_created_date <= as.Date("2020-02-21"))$posts_per_day))
                                                         
colnames(obesity_clarinet_count_per_day_date_restricted) <- c("y", "x1")
obesity_clarinet_count_per_day_date_restricted$y <- as.numeric(obesity_clarinet_count_per_day_date_restricted$y)
obesity_clarinet_count_per_day_date_restricted$x1 <- as.numeric(obesity_clarinet_count_per_day_date_restricted$x1)

dat <- zoo(obesity_clarinet_count_per_day_date_restricted,
           seq.Date(as.Date("2019-12-20"),
                    as.Date("2020-02-21"),
                    "day"))

pre_period <- as.Date(c("2019-12-20", "2020-01-20"))
post_period <- as.Date(c("2020-01-21", "2020-02-21"))
impact <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact)
summary(impact) #No difference after Jan. 20
```

## March 11, 2020 (WHO Pandemic)
```{r}
obesity_count_per_day <- rbind(obesity_count_per_day,
                                 c("2020-04-01", 0, "Obesity"))

obesity_count_per_day %<>%
  arrange(post_created_date)

obesity_clarinet_count_per_day_date_restricted_who <- as.data.frame(cbind(filter(obesity_count_per_day,
                                                                post_created_date >= as.Date("2020-02-11") &
                                                                  post_created_date <= as.Date("2020-04-12"))$posts_per_day,
                                                         filter(clarinet_count_per_day,
                                                                post_created_date >= as.Date("2020-02-11") &
                                                                  post_created_date <= as.Date("2020-04-12"))$posts_per_day))
                                                         
colnames(obesity_clarinet_count_per_day_date_restricted_who) <- c("y", "x1")
obesity_clarinet_count_per_day_date_restricted_who$y <- as.numeric(obesity_clarinet_count_per_day_date_restricted_who$y)
obesity_clarinet_count_per_day_date_restricted_who$x1 <- as.numeric(obesity_clarinet_count_per_day_date_restricted_who$x1)

dat <- zoo(obesity_clarinet_count_per_day_date_restricted_who,
           seq.Date(as.Date("2020-02-11"),
                    as.Date("2020-04-12"),
                    "day"))

pre_period <- as.Date(c("2020-02-11", "2020-03-11"))
post_period <- as.Date(c("2020-03-12", "2020-04-12"))
impact_who <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_who)
summary(impact_who) #Significant difference with non-health comparator
```

## May 19th, 2020 (Obesity linked with COVID-19)
```{r}
obesity_clarinet_count_per_day_date_restricted_obesity_linked <- as.data.frame(cbind(filter(obesity_count_per_day,
                                                                post_created_date >= as.Date("2020-04-19") &
                                                                  post_created_date <= as.Date("2020-06-20"))$posts_per_day,
                                                         filter(clarinet_count_per_day,
                                                                post_created_date >= as.Date("2020-04-19") &
                                                                  post_created_date <= as.Date("2020-06-20"))$posts_per_day))
                                                         
colnames(obesity_clarinet_count_per_day_date_restricted_obesity_linked) <- c("y", "x1")
obesity_clarinet_count_per_day_date_restricted_obesity_linked$y <- as.numeric(obesity_clarinet_count_per_day_date_restricted_obesity_linked$y)
obesity_clarinet_count_per_day_date_restricted_obesity_linked$x1 <- as.numeric(obesity_clarinet_count_per_day_date_restricted_obesity_linked$x1)

dat <- zoo(obesity_clarinet_count_per_day_date_restricted_obesity_linked,
           seq.Date(as.Date("2020-04-19"),
                    as.Date("2020-06-20"),
                    "day"))

pre_period <- as.Date(c("2020-04-19", "2020-05-19"))
post_period <- as.Date(c("2020-05-20", "2020-06-20"))
impact_obesity_linked <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_obesity_linked)
summary(impact_obesity_linked) #No significant difference after obesity linked
```

## October 2, 2020 (Trump gets COVID-19)
```{r}
obesity_clarinet_count_per_day_date_restricted_trump <- as.data.frame(cbind(filter(obesity_count_per_day,
                                                                post_created_date >= as.Date("2020-09-02") &
                                                                  post_created_date <= as.Date("2020-11-03"))$posts_per_day,
                                                         filter(clarinet_count_per_day,
                                                                post_created_date >= as.Date("2020-09-02") &
                                                                  post_created_date <= as.Date("2020-11-03"))$posts_per_day))
                                                         
colnames(obesity_clarinet_count_per_day_date_restricted_trump) <- c("y", "x1")
obesity_clarinet_count_per_day_date_restricted_trump$y <- as.numeric(obesity_clarinet_count_per_day_date_restricted_trump$y)
obesity_clarinet_count_per_day_date_restricted_trump$x1 <- as.numeric(obesity_clarinet_count_per_day_date_restricted_trump$x1)

dat <- zoo(obesity_clarinet_count_per_day_date_restricted_trump,
           seq.Date(as.Date("2020-09-02"),
                    as.Date("2020-11-03"),
                    "day"))

pre_period <- as.Date(c("2020-09-02", "2020-10-02"))
post_period <- as.Date(c("2020-10-03", "2020-11-03"))
impact_trump <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_trump)
summary(impact_trump) #Significant difference after Trump gets COVID-19 
```

# Interactions per Day
```{r}
obesity %<>%
  mutate(total_interactions_numeric = as.numeric(str_remove(total_interactions, " ")))

headaches %<>%
  mutate(total_interactions_numeric = as.numeric(str_remove(total_interactions, " ")))

clarinet %<>%
  mutate(total_interactions_numeric = as.numeric(str_remove(total_interactions, " ")))

obesity_interaction_per_day <- obesity %>%
  group_by(post_created_date) %>%
  summarise(interactions_per_day = sum(total_interactions_numeric, na.rm = TRUE)) %>%
  mutate(data_set = "Obesity")

headaches_interaction_per_day <- headaches %>%
  group_by(post_created_date) %>%
  summarise(interactions_per_day = sum(total_interactions_numeric, na.rm = TRUE)) %>%
  mutate(data_set = "Health Comparator")

clarinet_interaction_per_day <- clarinet %>%
  group_by(post_created_date) %>%
  summarise(interactions_per_day = sum(total_interactions_numeric, na.rm = TRUE)) %>%
  mutate(data_set = "Non-Health Comparator")

all_interactions_per_day <- rbind(obesity_interaction_per_day, headaches_interaction_per_day, clarinet_interaction_per_day)

all_interactions_per_day %>%
  mutate(data_set = factor(data_set, 
                           levels = c("Obesity",
                                      "Health Comparator",
                                      "Non-Health Comparator"))) %>%
  ggplot(aes(x = post_created_date,
             y = interactions_per_day,
             color = data_set)) +
  geom_point() +
  geom_vline(xintercept = as.Date("2020-01-20"),
             linetype = "dashed") + 
  geom_vline(xintercept = as.Date("2020-03-11"),
             linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-05-19"),
             linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-10-20"),
             linetype = "dashed") +
  theme_classic() +
  scale_color_aaas() + 
  labs(title = "Temporal Variations in Interactions Obesity-Related Content on Facebook\nRelative to Comparators",
       x = "Date (Year-Month)",
       y = "Interactions (Count)",
       color = "Data Set") +
  theme(legend.position = "bottom")
setwd("~/Documents/dartmouth/research/aim3_facebook_covid19_obesity/figures")
ggsave("211214_change_in_interactions_over_time_facebook.tiff", 
       width = 7.25,
       height = 4.51)
```

# BSTSM for Obesity vs. Health Comparator - # Interaction
## January 20th, 2020 (First US Case)
```{r}
headaches_interaction_per_day <- rbind(headaches_interaction_per_day,
                                 c("2020-01-01", 0, "Health Comparator"))

headaches_interaction_per_day %<>%
  arrange(post_created_date)

obesity_headaches_interaction_per_day_date_restricted <- as.data.frame(cbind(filter(obesity_interaction_per_day,
                                                                post_created_date >= as.Date("2019-12-20") &
                                                                  post_created_date <= as.Date("2020-02-21"))$interactions_per_day,
                                                         filter(headaches_interaction_per_day,
                                                                post_created_date >= as.Date("2019-12-20") &
                                                                  post_created_date <= as.Date("2020-02-21"))$interactions_per_day))
                                                         
colnames(obesity_headaches_interaction_per_day_date_restricted) <- c("y", "x1")
obesity_headaches_interaction_per_day_date_restricted$y <- as.numeric(obesity_headaches_interaction_per_day_date_restricted$y)
obesity_headaches_interaction_per_day_date_restricted$x1 <- as.numeric(obesity_headaches_interaction_per_day_date_restricted$x1)

dat <- zoo(obesity_headaches_interaction_per_day_date_restricted,
           seq.Date(as.Date("2019-12-20"),
                    as.Date("2020-02-21"),
                    "day"))

pre_period <- as.Date(c("2019-12-20", "2020-01-20"))
post_period <- as.Date(c("2020-01-21", "2020-02-21"))
impact <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact)
summary(impact) #No difference after Jan. 20
```

## March 11, 2020 (WHO Pandemic)
```{r}
obesity_interaction_per_day <- rbind(obesity_interaction_per_day,
                                 c("2020-04-01", 0, "Obesity"))

obesity_interaction_per_day %<>%
  arrange(post_created_date)

obesity_headaches_interaction_per_day_date_restricted_who <- as.data.frame(cbind(filter(obesity_interaction_per_day,
                                                                post_created_date >= as.Date("2020-02-11") &
                                                                  post_created_date <= as.Date("2020-04-12"))$interactions_per_day,
                                                         filter(headaches_interaction_per_day,
                                                                post_created_date >= as.Date("2020-02-11") &
                                                                  post_created_date <= as.Date("2020-04-12"))$interactions_per_day))
                                                         
colnames(obesity_headaches_interaction_per_day_date_restricted_who) <- c("y", "x1")
obesity_headaches_interaction_per_day_date_restricted_who$y <- as.numeric(obesity_headaches_interaction_per_day_date_restricted_who$y)
obesity_headaches_interaction_per_day_date_restricted_who$x1 <- as.numeric(obesity_headaches_interaction_per_day_date_restricted_who$x1)

dat <- zoo(obesity_headaches_interaction_per_day_date_restricted_who,
           seq.Date(as.Date("2020-02-11"),
                    as.Date("2020-04-12"),
                    "day"))

pre_period <- as.Date(c("2020-02-11", "2020-03-11"))
post_period <- as.Date(c("2020-03-12", "2020-04-12"))
impact_who <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_who)
summary(impact_who) #Significantly fewer interaction
```

## May 19th, 2020 (Obesity linked with COVID-19)
```{r}
obesity_headaches_interaction_per_day_date_restricted_obesity_linked <- as.data.frame(cbind(filter(obesity_interaction_per_day,
                                                                post_created_date >= as.Date("2020-04-19") &
                                                                  post_created_date <= as.Date("2020-06-20"))$interactions_per_day,
                                                         filter(headaches_interaction_per_day,
                                                                post_created_date >= as.Date("2020-04-19") &
                                                                  post_created_date <= as.Date("2020-06-20"))$interactions_per_day))
                                                         
colnames(obesity_headaches_interaction_per_day_date_restricted_obesity_linked) <- c("y", "x1")
obesity_headaches_interaction_per_day_date_restricted_obesity_linked$y <- as.numeric(obesity_headaches_interaction_per_day_date_restricted_obesity_linked$y)
obesity_headaches_interaction_per_day_date_restricted_obesity_linked$x1 <- as.numeric(obesity_headaches_interaction_per_day_date_restricted_obesity_linked$x1)

dat <- zoo(obesity_headaches_interaction_per_day_date_restricted_obesity_linked,
           seq.Date(as.Date("2020-04-19"),
                    as.Date("2020-06-20"),
                    "day"))

pre_period <- as.Date(c("2020-04-19", "2020-05-19"))
post_period <- as.Date(c("2020-05-20", "2020-06-20"))
impact_obesity_linked <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_obesity_linked)
summary(impact_obesity_linked) #No significant difference after obesity linked
```

## October 2, 2020 (Trump gets COVID-19)
```{r}
headaches_interaction_per_day <- rbind(headaches_interaction_per_day,
                                 c("2020-11-01", 0, "Health Comparator"))

headaches_interaction_per_day %<>%
  arrange(post_created_date)

obesity_headaches_interaction_per_day_date_restricted_trump <- as.data.frame(cbind(filter(obesity_interaction_per_day,
                                                                post_created_date >= as.Date("2020-09-02") &
                                                                  post_created_date <= as.Date("2020-11-03"))$interactions_per_day,
                                                         filter(headaches_interaction_per_day,
                                                                post_created_date >= as.Date("2020-09-02") &
                                                                  post_created_date <= as.Date("2020-11-03"))$interactions_per_day))
                                                         
colnames(obesity_headaches_interaction_per_day_date_restricted_trump) <- c("y", "x1")
obesity_headaches_interaction_per_day_date_restricted_trump$y <- as.numeric(obesity_headaches_interaction_per_day_date_restricted_trump$y)
obesity_headaches_interaction_per_day_date_restricted_trump$x1 <- as.numeric(obesity_headaches_interaction_per_day_date_restricted_trump$x1)

dat <- zoo(obesity_headaches_interaction_per_day_date_restricted_trump,
           seq.Date(as.Date("2020-09-02"),
                    as.Date("2020-11-03"),
                    "day"))

pre_period <- as.Date(c("2020-09-02", "2020-10-02"))
post_period <- as.Date(c("2020-10-03", "2020-11-03"))
impact_trump <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_trump)
summary(impact_trump) #No significant difference after Trump gets COVID-19 
```

# BSTSM for Obesity vs. Non-Health Comparator - #Interactions
## January 20th, 2020 (First US Case)
```{r}
obesity_clarinet_interaction_per_day_date_restricted <- as.data.frame(cbind(filter(obesity_interaction_per_day,
                                                                post_created_date >= as.Date("2019-12-20") &
                                                                  post_created_date <= as.Date("2020-02-21"))$interactions_per_day,
                                                         filter(clarinet_interaction_per_day,
                                                                post_created_date >= as.Date("2019-12-20") &
                                                                  post_created_date <= as.Date("2020-02-21"))$interactions_per_day))
                                                         
colnames(obesity_clarinet_interaction_per_day_date_restricted) <- c("y", "x1")
obesity_clarinet_interaction_per_day_date_restricted$y <- as.numeric(obesity_clarinet_interaction_per_day_date_restricted$y)
obesity_clarinet_interaction_per_day_date_restricted$x1 <- as.numeric(obesity_clarinet_interaction_per_day_date_restricted$x1)

dat <- zoo(obesity_clarinet_interaction_per_day_date_restricted,
           seq.Date(as.Date("2019-12-20"),
                    as.Date("2020-02-21"),
                    "day"))

pre_period <- as.Date(c("2019-12-20", "2020-01-20"))
post_period <- as.Date(c("2020-01-21", "2020-02-21"))
impact <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact)
summary(impact) #Significant change after January 20th 
```

## March 11, 2020 (WHO Pandemic)
```{r}
obesity_interaction_per_day <- rbind(obesity_interaction_per_day,
                                 c("2020-04-01", 0, "Obesity"))

obesity_interaction_per_day %<>%
  arrange(post_created_date)

obesity_clarinet_interaction_per_day_date_restricted_who <- as.data.frame(cbind(filter(obesity_interaction_per_day,
                                                                post_created_date >= as.Date("2020-02-11") &
                                                                  post_created_date <= as.Date("2020-04-12"))$interactions_per_day,
                                                         filter(clarinet_interaction_per_day,
                                                                post_created_date >= as.Date("2020-02-11") &
                                                                  post_created_date <= as.Date("2020-04-12"))$interactions_per_day))
                                                         
colnames(obesity_clarinet_interaction_per_day_date_restricted_who) <- c("y", "x1")
obesity_clarinet_interaction_per_day_date_restricted_who$y <- as.numeric(obesity_clarinet_interaction_per_day_date_restricted_who$y)
obesity_clarinet_interaction_per_day_date_restricted_who$x1 <- as.numeric(obesity_clarinet_interaction_per_day_date_restricted_who$x1)

dat <- zoo(obesity_clarinet_interaction_per_day_date_restricted_who,
           seq.Date(as.Date("2020-02-11"),
                    as.Date("2020-04-12"),
                    "day"))

pre_period <- as.Date(c("2020-02-11", "2020-03-11"))
post_period <- as.Date(c("2020-03-12", "2020-04-12"))
impact_who <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_who)
summary(impact_who) #Significantly fewer interaction
```

## May 19th, 2020 (Obesity linked with COVID-19)
```{r}
obesity_clarinet_interaction_per_day_date_restricted_who <- as.data.frame(cbind(filter(obesity_interaction_per_day,
                                                                post_created_date >= as.Date("2020-04-19") &
                                                                  post_created_date <= as.Date("2020-06-20"))$interactions_per_day,
                                                         filter(clarinet_interaction_per_day,
                                                                post_created_date >= as.Date("2020-04-19") &
                                                                  post_created_date <= as.Date("2020-06-20"))$interactions_per_day))
                                                         
colnames(obesity_clarinet_interaction_per_day_date_restricted_who) <- c("y", "x1")
obesity_clarinet_interaction_per_day_date_restricted_who$y <- as.numeric(obesity_clarinet_interaction_per_day_date_restricted_who$y)
obesity_clarinet_interaction_per_day_date_restricted_who$x1 <- as.numeric(obesity_clarinet_interaction_per_day_date_restricted_who$x1)

dat <- zoo(obesity_clarinet_interaction_per_day_date_restricted_who,
           seq.Date(as.Date("2020-04-19"),
                    as.Date("2020-06-20"),
                    "day"))

pre_period <- as.Date(c("2020-04-19", "2020-05-19"))
post_period <- as.Date(c("2020-05-20", "2020-06-20"))
impact_obesity_linked <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_obesity_linked)
summary(impact_obesity_linked) #No significant difference after obesity linked
```

## October 2, 2020 (Trump gets COVID-19)
```{r}
obesity_clarinet_interaction_per_day_date_restricted_trump <- as.data.frame(cbind(filter(obesity_interaction_per_day,
                                                                post_created_date >= as.Date("2020-09-02") &
                                                                  post_created_date <= as.Date("2020-11-03"))$interactions_per_day,
                                                         filter(clarinet_interaction_per_day,
                                                                post_created_date >= as.Date("2020-09-02") &
                                                                  post_created_date <= as.Date("2020-11-03"))$interactions_per_day))
                                                         
colnames(obesity_clarinet_interaction_per_day_date_restricted_trump) <- c("y", "x1")
obesity_clarinet_interaction_per_day_date_restricted_trump$y <- as.numeric(obesity_clarinet_interaction_per_day_date_restricted_trump$y)
obesity_clarinet_interaction_per_day_date_restricted_trump$x1 <- as.numeric(obesity_clarinet_interaction_per_day_date_restricted_trump$x1)

dat <- zoo(obesity_clarinet_interaction_per_day_date_restricted_trump,
           seq.Date(as.Date("2020-09-02"),
                    as.Date("2020-11-03"),
                    "day"))

pre_period <- as.Date(c("2020-09-02", "2020-10-02"))
post_period <- as.Date(c("2020-10-03", "2020-11-03"))
impact_trump <- CausalImpact(dat, 
                       pre_period, 
                       post_period)
plot(impact_trump)
summary(impact_trump) #No significant difference after Trump gets COVID-19 
```

